# Category analysis

```{r external-code, cashe=FALSE, echo=FALSE}
knitr::read_chunk('categoryExploration.R')
```
## Q0: How many unique categories?

### Ans: 31

## Q1: We know some coupons belong to several categories, but what is the maximum number of categories they have?

### Ans: 5

```{r Q1, echo=FALSE}
```
## Q2: Is coupon usage rate and the basketValue related to the number of categories it belongs to?

### Ans: Not quite significant but yes. For example, for coupons in `couponID2`, if their `categoryIDs2` has five categories, then their coupon usage rate seems to be much lower.

Stat for `categoryIDs1`. Row i stands for `categoryIDs1` that has i categories.

```{r Q2-1, echo=FALSE}
```

Stat for `categoryIDs2`

```{r Q2-2, echo=FALSE}
```

Stat for `categoryIDs3`

```{r Q2-3, echo=FALSE}
```

## Q3: Is the coupon usage rate and the basketValue related to categories?

### Ans: Yes. For exmaple, for coupoons in `couponID2`, if they belong to `category8`, then the coupon usage rate is as high as 0.42!

Stat for `categoryIDs1`

```{r Q3-1, echo=FALSE}
```

Stat for `categoryIDs2`

```{r Q3-2, echo=FALSE}
```

Stat for `categoryIDs3`

```{r Q3-3, echo=FALSE}
```

