---
title: Categorical Similarity Measures
titleshort: CatSims
author: Ian Mouzon
authorshort: imouzon
contact: imouzon@iastate.edu
grouplong: Iowa State University's 2015 Data Mining Cup Team
groupshort: DMC@ISU
leader: One Week Left 
leadershort: One Week Left
semester: Spring 2015
assignment: 
duedate: May 8, 2015
output:
  usefulR::hw_format:
  keep_tex: true
---

<!--- # (R code (No Results in Document)) -->
```{r set-parent, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   #set up knitr
   #devtools::install_github('imouzon/usefulR')
   library(usefulR)

   #set working directory
   working.dir = "~/dmc2015/ian"
   setwd(working.dir)

   #compile the document to PDF
   if(FALSE) 
      rmarkdown::render("./categorical_similarity.Rmd")
```
I am using the following packages:
<!--- # (R code (No Results in Document))-->
```{r paks, echo=TRUE, cache=FALSE, message=FALSE, tidy=FALSE, include=TRUE}
   library(ggplot2)
   library(lubridate)
   library(xtable)
   library(foreach)
   library(rCharts)
   library(magrittr)
   library(tidyr)
   library(dplyr)
   library(reshape2)
   library(gtools)
   library(sqldf)
   library(missForest)
   source("./R/renm.R")
```
and my working directory is set to \verb!dmc2015/ian!.

# Categorical Similarity
Oh My Gosh - did you know that you can compare categorical variables to each other?
You can create kind of like a distance on them.

One simple example based on the Jaccard Measure:

Let $\mathbf{u}$ and $\mathbf{v}$ be two multidimensional categorical variables
taking values in $A = \{a_1, a_2, \ldots, a_n\}$. Then we can think of these
as subsets of the the set $A$ in which case we can describe a similarity
between the coupons using
$$
   J(\mathbf{u}, \mathbf{v}) = \dfrac{| \mathbf{u} \cap \mathbf{v} |}{ \mathbf{u} \cup \mathbf{v}}
$$
In this document I am calculating some of these features for the categorical variables \verb!categoryIDs!.

# Getting Tranthe Data and Manipulations 
I am using our new clean data - so should you
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
   d = readRDS("../data/clean_data/universalCleanData.rds")
```

I can melt the columns by coupon using the following:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   source("./r/stackCoupons2.R")
   dm = stackCoupons2(d,idcols = c(1:4,32:49)) 
```

I and can split the columns of product group using:
<!--- splitcols: R code (No Results in Document) -->
```{r splitcols,cache=FALSE}
   source("./r/splitColumn.R")
   dmc = splitColumn(dm,"categoryIDs","orderID",splitby=":") 
   dmcs = dmc[,c(1,23,32:37)] %>% 
      mutate(couponNum = as.numeric(gsub("cpn","",couponID))) %>% 
      arrange(orderID,couponID)

   #saveRDS(list("d" = "d", "dm" = dm,"dmc" = dmc),file="./written_data/universalCleanData_wide_melt_split.rds")
   #the number of coupons
   ncpns = length(unique(dmc$couponID))
```
Consider the unique coupon IDs and create a matrix with the columns 0 to 1 for whether or
not the coupon has the given category:
<!--- newmats: R code (No Results in Document) -->
```{r newmats,cache=FALSE}
   dmcsu = unique(dmcs[,c(2,9,4:8)]) %>% arrange(couponNum)

   dmcsuc = matrix(NA,nrow=nrow(dmcsu),ncol=31)
   for(i in 1:nrow(dmcsuc)) dmcsuc[i,] = 1*(paste0('cat',1:31) %in% dmcsu[i,2:6])

   catIndMat = dmcsu[,"couponID"] %>% cbind(data.frame(dmcsuc))
   names(catIndMat) = c("couponID",paste0("cat",1:31))
```
and save the jaccard matrix from this:
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE}
   #these are the jaccard similarities
   jaccard_func = function(cpn1,cpn2) sum(cpn1 * cpn2)/sum(as.numeric(cpn1 + cpn2 > 0))

   dmcsuck = matrix(0,ncpns,ncpns)
   for(i in 1:ncpns) for(j in i:ncpns) dmcsuck[i,j] = jaccard_func(dmcsuc[i,],dmcsuc[j,])
```

# Jaccard Similarity Used To Describe Order
We can use these jaccard similaritys to describe our orders. Consider, for example,
the mean Jaccard similarity:

<!--- chunk-label: R code (No Results in Document) -->
```{r usejaccard, cache=FALSE}
   dmcsucks = d %>% arrange(orderID) %>% select(couponID1,couponID2,couponID3)
 
   JaccardSummary= function(i){
      x = as.numeric(dmcsucks[i,])
      rows = combn(x,2)[1,]
      cols = combn(x,2)[2,]
      sapply(1:3,function(j) dmcsuck[rows[j],cols[j]])
   }

   jac.d = d %>% select(orderID) %>% 
      cbind(t(sapply(1:nrow(dmcsucks), function(i) JaccardSummary(i)))) %>%
      data.frame %>%
      renm(c("orderID","jaccard12","jaccard13","jaccard23"))

   head(jac.d)
```

# Term Frequency, Document Frequency

We can also consider comparing the coupons like a set of documents, using \verb!tf-idf!:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   #parameters
   N = ncpns
   nt = colSums(dmcsuc)

   #term frequency
   ##raw frequency
   ftd = dmcsuc

   ##log normalization
   lnormM = log(2)*dmcsuc

   #document frequency
   ##inverse frequency
   ivf = log(N/nt)

   ##inverse frequency smooth
   lnorm = log(1 + N/nt)

   ##inverse frequency max
   invmax = log(1 + max(nt)/nt)

   ##probabilistic inverse frequency
   pif = log((N - nt)/nt)

   ftd_lnorm = matrix(sapply(1:N, function(i) ftd[i,]*lnorm),nrow=N,byrow=TRUE)
   ftd_ivf = matrix(sapply(1:N, function(i) ftd[i,]*ivf),nrow=N,byrow=TRUE)
   ftd_invmax = matrix(sapply(1:N, function(i) ftd[i,]*invmax),nrow=N,byrow=TRUE)
   ftd_pif = matrix(sapply(1:N, function(i) ftd[i,]*pif),nrow=N,byrow=TRUE)

   lnorm_lnorm = matrix(sapply(1:N, function(i) lnormM[i,]*lnorm),nrow=N,byrow=TRUE)
   lnorm_ivf = matrix(sapply(1:N, function(i) lnormM[i,]*ivf),nrow=N,byrow=TRUE)
   lnorm_invmax = matrix(sapply(1:N, function(i) lnormM[i,]*invmax),nrow=N,byrow=TRUE)
   lnorm_pif = matrix(sapply(1:N, function(i) lnormM[i,]*pif),nrow=N,byrow=TRUE)
```

# Cosine Similarity
And we can get the cosine similiarty matrix:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   self_multiply = function(X) X %*% t(X)

   cosine_similarity = function(sim_mat){
      (sim_mat %*% t(sim_mat)) / (sim_mat %*% t(sim_mat) %>% sqrt %>% diag %>% matrix(ncol=1) %>% self_multiply)
   }

   sim_ftd_lnorm = cosine_similarity(ftd_lnorm)
   sim_ftd_ivf = cosine_similarity(ftd_ivf)
   sim_ftd_invmax = cosine_similarity(ftd_invmax)
   sim_ftd_pif = cosine_similarity(ftd_pif)

   sim_lnorm_lnorm = cosine_similarity(lnorm_lnorm)
   sim_lnorm_ivf = cosine_similarity(lnorm_ivf)
   sim_lnorm_invmax = cosine_similarity(lnorm_invmax)
   sim_lnorm_pif = cosine_similarity(lnorm_pif)
```
which we can calculate as follows:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   dmcsucks = d %>% arrange(orderID) %>% select(couponID1,couponID2,couponID3)
 
   CosSimSummary= function(i,sim_mat){
      x = as.numeric(dmcsucks[i,])
      rows = combn(x,2)[1,]
      cols = combn(x,2)[2,]
      sapply(1:3,function(j) sim_mat[rows[j],cols[j]])
   }

   #sim_ftd_lnorm
   cos.d1 = d %>% select(orderID) %>% cbind(t(sapply(1:nrow(dmcsucks), function(i) CosSimSummary(i,sim_ftd_lnorm)))) %>% data.frame %>% renm(c("orderID", "sim_ftd_lnorm_cosSim12", "sim_ftd_lnorm_cosSim13", "sim_ftd_lnorm_cos.sim23"))

   #sim_ftd_ivf
   cos.d2 = d %>% select(orderID) %>% cbind(t(sapply(1:nrow(dmcsucks), function(i) CosSimSummary(i,sim_ftd_ivf)))) %>% data.frame %>% renm(c("orderID", "sim_ftd_ivf_cosSim12", "sim_ftd_ivf_cosSim13", "sim_ftd_ivf_cos.sim23"))

   #sim_ftd_infmax
   cos.d3 = d %>% select(orderID) %>% cbind(t(sapply(1:nrow(dmcsucks), function(i) CosSimSummary(i,sim_ftd_invmax)))) %>% data.frame %>% renm(c("orderID", "sim_ftd_invmax_cosSim12", "sim_ftd_invmax_cosSim13", "sim_ftd_invmax_cos.sim23"))

   #sim_lnorm_pif
   cos.d4 = d %>% select(orderID) %>% cbind(t(sapply(1:nrow(dmcsucks), function(i) CosSimSummary(i,sim_ftd_pif)))) %>% data.frame %>% renm(c("orderID", "sim_ftd_pif_cosSim12", "sim_ftd_pif_cosSim13", "sim_ftd_pif_cos.sim23"))

   #sim_lnorm_lnorm
   cos.d5 = d %>% select(orderID) %>% cbind(t(sapply(1:nrow(dmcsucks), function(i) CosSimSummary(i,sim_lnorm_lnorm)))) %>% data.frame %>% renm(c("orderID", "sim_lnorm_lnorm_cosSim12", "sim_lnorm_lnorm_cosSim13", "sim_lnorm_lnorm_cos.sim23"))

   #sim_lnorm_ivf
   cos.d6 = d %>% select(orderID) %>% cbind(t(sapply(1:nrow(dmcsucks), function(i) CosSimSummary(i,sim_lnorm_ivf)))) %>% data.frame %>% renm(c("orderID", "sim_lnorm_ivf_cosSim12", "sim_lnorm_ivf_cosSim13", "sim_lnorm_ivf_cos.sim23"))

   #sim_lnorm_infmax
   cos.d7 = d %>% select(orderID) %>% cbind(t(sapply(1:nrow(dmcsucks), function(i) CosSimSummary(i,sim_lnorm_invmax)))) %>% data.frame %>% renm(c("orderID", "sim_lnorm_invmax_cosSim12", "sim_lnorm_invmax_cosSim13", "sim_lnorm_invmax_cos.sim23"))

   #sim_lnorm_pif
   cos.d8 = d %>% select(orderID) %>% cbind(t(sapply(1:nrow(dmcsucks), function(i) CosSimSummary(i,sim_lnorm_pif)))) %>% data.frame %>% renm(c("orderID", "sim_lnorm_pif_cosSim12", "sim_lnorm_pif_cosSim13", "sim_lnorm_pif_cos.sim23"))
```

#Results
Consider the chances that coupons were used when the coupons had more similarity. 
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   simFeatures = function(sim_mat){
      d_A = dm %>%
          select(orderID,couponID,couponCol,couponUsed) %>%
          renm(c("orderID","couponIDA","couponColA","couponUsedA")) %>%
          left_join(sim_mat,by="orderID") %>%
          gather(sim_meas,value,-orderID,-couponIDA,-couponColA,-couponUsedA) %>%
          arrange(orderID,couponColA) %>%
          filter((grepl("12",sim_meas) & couponColA == 1) | (grepl("13",sim_meas) & couponColA == 1) | (grepl("23",sim_meas) & couponColA == 2))

      d_B = dm %>%
          select(orderID,couponID,couponCol,couponUsed) %>%
          renm(c("orderID","couponIDB","couponColB","couponUsedB")) %>%
          left_join(sim_mat,by="orderID") %>%
          gather(sim_meas,value,-orderID,-couponIDB,-couponColB,-couponUsedB) %>%
          arrange(orderID,couponColB) %>%
          filter((grepl("23",sim_meas) & couponColB == 3) | (grepl("13",sim_meas) & couponColB == 3) | (grepl("12",sim_meas) & couponColB == 2))

      d_AB = d_A %>% left_join(d_B,by=c("orderID","sim_meas","value")) %>% mutate(nUsed = factor(couponUsedA + couponUsedB))

      ggplot(data=d_AB,aes(x=value,color=factor(nUsed))) + geom_density()

      p = d_AB %>% filter(!is.na(couponUsedA)) %>% 
         mutate(usedColA = paste0("coupon",couponColA,"Used=",couponUsedA)) %>%
         mutate(usedColB = paste0("coupon",couponColB,"Used=",couponUsedB)) %>%
         mutate(usedA = paste0("couponAUsed=",couponUsedA)) %>%
         mutate(usedB = paste0("couponBUsed=",couponUsedB)) %>%
         mutate(fill = paste0("cpn",couponColA,"Xcpn",couponColB)) %>%
         mutate(nUsed = factor(couponUsedA + couponUsedB)) %>%
         mutate(similarity= value) 

      p1 = p %>% ggplot(aes(fill=usedA,x=similarity,alpha=.2)) + facet_grid(usedB~.,scales="free_y") + geom_density()

      p2 = p %>% ggplot(aes(fill=interaction(usedA,usedB),x=fill,y=log(similarity),alpha=.2)) + geom_boxplot()
      
      return(list(p1 = p1, p2 = p2))
   }
```

## Jaccard Measure
<!--- chunk-label: R code (No Results in Document) -->
```{r fig.width=9,fig.height=5,out.width='.9\\linewidth',out.height='.5\\linewidth'}
   #figures
   figures = simFeatures(jac.d)

   #print
   print(figures$p1)
   print(figures$p2)

   #save
   saveRDS(jac.d,file="../features/feature_files/universal/jaccard_similarity.rds")
```

## tf-idf using ftd and lnorm
<!--- chunk-label: R code (No Results in Document) -->
```{r fig.width=9,fig.height=5,out.width='.9\\linewidth',out.height='.5\\linewidth'}
   # similarity matrix
   sim_mat = cos.d1

   #figures
   figures = simFeatures(sim_mat)

   #print
   print(figures$p1)
   print(figures$p2)

   #save
   saveRDS(sim_mat,file="../features/feature_files/universal/ftd_lnorm_similarity.rds")
```

## tf-idf using ftd and ivf
<!--- chunk-label: R code (No Results in Document) -->
```{r fig.width=9,fig.height=5,out.width='.9\\linewidth',out.height='.5\\linewidth'}
   # similarity matrix
   sim_mat = cos.d2

   #figures
   figures = simFeatures(sim_mat)

   #print
   print(figures$p1)
   print(figures$p2)

   #save
   saveRDS(sim_mat,file="../features/feature_files/universal/ftd_ivf_similarity.rds")
```

## tf-idf using ftd and invmax
<!--- chunk-label: R code (No Results in Document) -->
```{r fig.width=9,fig.height=5,out.width='.9\\linewidth',out.height='.5\\linewidth'}
   # similarity matrix
   sim_mat = cos.d3

   #figures
   figures = simFeatures(sim_mat)

   #print
   print(figures$p1)
   print(figures$p2)

   #save
   saveRDS(sim_mat,file="../features/feature_files/universal/ftd_invmax_similarity.rds")
```

## tf-idf using ftd and pif
<!--- chunk-label: R code (No Results in Document) -->
```{r fig.width=9,fig.height=5,out.width='.9\\linewidth',out.height='.5\\linewidth'}
   # similarity matrix
   sim_mat = cos.d4

   #figures
   figures = simFeatures(sim_mat)

   #print
   print(figures$p1)
   print(figures$p2)

   #save
   saveRDS(sim_mat,file="../features/feature_files/universal/ftd_pif_similarity.rds")
```

## tf-idf using lnorm and lnorm
<!--- chunk-label: R code (No Results in Document) -->
```{r fig.width=9,fig.height=5,out.width='.9\\linewidth',out.height='.5\\linewidth'}
   # similarity matrix
   sim_mat = cos.d5

   #figures
   figures = simFeatures(sim_mat)

   #print
   print(figures$p1)
   print(figures$p2)

   #save
   saveRDS(sim_mat,file="../features/feature_files/universal/lnorm_lnorm_similarity.rds")
```

## tf-idf using lnorm and ivf
<!--- chunk-label: R code (No Results in Document) -->
```{r fig.width=9,fig.height=5,out.width='.9\\linewidth',out.height='.5\\linewidth'}
   # similarity matrix
   sim_mat = cos.d6

   #figures
   figures = simFeatures(sim_mat)

   #print
   print(figures$p1)
   print(figures$p2)

   #save
   saveRDS(sim_mat,file="../features/feature_files/universal/lnorm_ivf_similarity.rds")
```

## tf-idf using lnorm and invmax
<!--- chunk-label: R code (No Results in Document) -->
```{r fig.width=9,fig.height=5,out.width='.9\\linewidth',out.height='.5\\linewidth'}
   # similarity matrix
   sim_mat = cos.d7

   #figures
   figures = simFeatures(sim_mat)

   #print
   print(figures$p1)
   print(figures$p2)

   #save
   saveRDS(sim_mat,file="../features/feature_files/universal/lnorm_invmax_similarity.rds")
```

## tf-idf using lnorm and pif
<!--- chunk-label: R code (No Results in Document) -->
```{r fig.width=9,fig.height=5,out.width='.9\\linewidth',out.height='.5\\linewidth'}
   # similarity matrix
   sim_mat = cos.d8

   #figures
   figures = simFeatures(sim_mat)

   #print
   print(figures$p1)
   print(figures$p2)

   #save
   saveRDS(sim_mat,file="../features/feature_files/universal/lnorm_pif_similarity.rds")
```
