---
title: Categorical Similarity Measures
titleshort: CatSims
author: Ian Mouzon
authorshort: imouzon
contact: imouzon@iastate.edu
grouplong: Iowa State University's 2015 Data Mining Cup Team
groupshort: DMC@ISU
leader:  
leadershort: 
semester: Spring 2015
assignment: 
duedate: May 8, 2015
output:
  usefulR::hw_format:
  keep_tex: true
---

<!--- # (R code (No Results in Document)) -->
```{r set-parent, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   #set up knitr
   #devtools::install_github('imouzon/usefulR')
   library(usefulR)

   #set working directory
   working.dir = "~/dmc2015/ian"
   setwd(working.dir)

   #compile the document to PDF
   if(FALSE) 
      rmarkdown::render("./categorical_similarity.Rmd")
```

# Categorical Similarity
Oh My Gosh - did you know that you can compare categorical variables to each other?
You can create kind of like a distance on them.

One simple example based on the Jaccard Measure:

Let $\mathbf{u}$ and $\mathbf{v}$ be two multidimensional categorical variables
taking values in $A = \{a_1, a_2, \ldots, a_n\}$. Then we can think of these
as subsets of the the set $A$ in which case we can describe a similarity
between the coupons using
$$
   J(\mathbf{u}, \mathbf{v}) = \dfrac{| \mathbf{u} \cap \mathbf{v} |}{ \mathbf{u} \cup \mathbf{v}}
$$
In this document I am calculating some of these features for the categorical variables \verb!categoryIDs!.

# Reading the Data
I am using our new clean data - so should you
<!--- chunk-label: R code (No Results in Document) -->
```{r chunk-label,cache=FALSE}
   d = readRDS("../data/clean_data/.DS_Store
   
```

