---
title: Category IDs
titleshort: Gathering General Features
instructions: 
author: Ian Mouzon
authorshort: Mouzon
contact: imouzon@iastate.edu
grouplong: Machine Learning
groupshort: STAT 602
leader: Dr. Stephen Vardeman
leadershort: Vardeman
semester: Spring 2014
assignment: Problem 1 - 5
duedate: Monday May 4, 2015
output:
  usefulR::hw_format
---
<!--- # (R code (No Results in Document))-->
```{r set-parent, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   # devtools::install_github("imouzon/usefulR")
   library(usefulR)
   working.dir = "/Users/user/dmc2015/ian"
   setwd(working.dir)

   #set up file locations
   source("./R/renm.R")

   if(FALSE)
      rmarkdown::render("~/dmc2015/ian/catID_features.rmd")
```

I am using the following packages:
<!--- # (R code (No Results in Document))-->
```{r paks, echo=TRUE, cache=FALSE, message=FALSE, tidy=FALSE, include=TRUE}
   library(ggplot2)
   library(lubridate)
   library(xtable)
   library(foreach)
   library(rCharts)
   library(magrittr)
   library(tidyr)
   library(dplyr)
   library(reshape2)
   library(gtools)
   library(sqldf)
   library(missForest)
```
and my working directory is set to \verb!dmc2015/ian!.

# Reading the Data
I am working from the current feature matrix:
<!---  readFeatMat: R code (Code in Document) -->
```{r readFeatMat, echo=TRUE, cache=FALSE, tidy=FALSE, include = TRUE}
   featMat = readRDS("~/dmc2015/data/featureMatrix/old/featMat_v2.0.rds")
   trn = featMat$train
   cls = featMat$class

   #Also reading the melted train and test sets
   trn.m = read.csv("~/dmc2015/data/clean_data/melted_train_simple_name.csv")
   cls.m = read.csv("~/dmc2015/data/clean_data/melted_test_simple_name.csv")

   stack.trn = trn.m
   stack.trn$dsn = "trn"

   stack.cls = cls.m
   stack.cls$dsn = "cls"

   stack.m = rbind(stack.trn,stack.cls)

   stack.m$dsn = factor(stack.m$dsn,levels=c('trn','cls'))
```

In case I need to reference the raw data, I will read that too:
<!---  readRaw: R code (Code in Document) -->
```{r readRaw, echo=TRUE, cache=FALSE, tidy=FALSE, include = TRUE}
   raw.trn = read.csv("~/dmc2015/data/clean_data/train_simple_name.csv")
   raw.cls = read.csv("~/dmc2015/data/clean_data/test_simple_name.csv")
```

<!--- (splitcols: R code (No Results in Document))-->
```{r splitcols,echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   source("~/dmc2015/ian/R/splitColumn.R")
   stack.m$categoryIDs = as.character(stack.m$categoryIDs)
   splitCats = splitColumn(stack.m,"categoryIDs","orderID",splitby=":")

   melt.cats = splitCats[,c(1,15:21)] %>% 
      gather(variable,value,-orderID,-couponCol,-dsn) %>% 
      arrange(orderID,couponCol,dsn) %>%
      select(-variable) %>%
      filter(!is.na(value)) 

   catFreq = melt.cats %>% 
      with(table(value)) %>% 
      data.frame %>% 
      arrange(-Freq) %>% 
      renm(c("catID","nTotal"))

   catFreq = melt.cats %>% with(table(value,couponCol)) %>% 
      data.frame %>% 
      arrange(-Freq) %>% 
      renm(c("catID","couponCol","nTotal")) %>%
      spread(couponCol,nTotal) %>%
      renm(c("catID","nTotalCol1","nTotalCol2","nTotalCol3")) %>%
      full_join(catFreq,by="catID")

   #get order rates where we know the order outcome (i.e., training set)
   trn.m$categoryIDs = as.character(trn.m$categoryIDs)
   split.trn = splitColumn(trn.m,"categoryIDs","orderID",splitby=":")

   melt.trn = split.trn[,c(1,14:20)] %>% 
      gather(variable,value,-orderID,-couponCol,-couponUsed) %>% 
      arrange(orderID,couponCol) %>% 
      select(-variable) %>% 
      filter(!is.na(value))

   trnFreq = melt.trn %>% 
      with(table(value,couponCol)) %>% 
      data.frame %>% 
      arrange(-Freq) %>% 
      renm(c("catID","couponCol","nTotalUsed")) %>%
      spread(couponCol,nTotalUsed) %>%
      renm(c("catID","nTotalCol1","nTotalCol2","nTotalCol3"))

   trnFreq$nTotal = with(trnFreq,nTotalCol1 + nTotalCol2 + nTotalCol3)

   trnFreq = melt.trn %>% 
      filter(couponUsed == 1) %>% 
      with(table(value,couponCol)) %>% 
      data.frame %>% 
      arrange(-Freq) %>% 
      renm(c("catID","couponCol","nTotalUsed")) %>%
      spread(couponCol,nTotalUsed) %>%
      renm(c("catID","nTotalUsedCol1","nTotalUsedCol2","nTotalUsedCol3")) %>%
      full_join(trnFreq,by="catID")

   trnFreq[31,2:4] = 0

   trnFreq$nTotalUsed = with(trnFreq,nTotalUsedCol1 + nTotalUsedCol2 + nTotalUsedCol3)

   trnFreq$propUsedCol1 = trnFreq$nTotalUsedCol1/trnFreq$nTotalCol1
   trnFreq$propUsedCol2 = trnFreq$nTotalUsedCol2/trnFreq$nTotalCol2
   trnFreq$propUsedCol3 = trnFreq$nTotalUsedCol3/trnFreq$nTotalCol3
   trnFreq$propUsed = trnFreq$nTotalUsed/trnFreq$nTotal

   #There are some missing values in this use frequenct matrix (this is to be expected) I can impute the values using missForest
   impute.missing1000 = missForest(trnFreq[,2:ncol(trnFreq)],maxiter=10, ntree = 1000, verbose =TRUE, mtry = 5, replace = TRUE)

   trnFreq.imp = trnFreq[,1] %>% cbind(impute.missing1000$ximp)
   names(trnFreq.imp)[1] = "catID"
   
   catFreq = catFreq %>% full_join(trnFreq.imp[,c("catID","propUsedCol1","propUsedCol2","propUsedCol3","propUsed")],by="catID")  %>% arrange(catID)

   qplot(catID, propUsed,size=nTotal, data=catFreq)
```
#Getting the results for all 2, 3, 4, and 5 way combinations of categories:
We can repeat what we did above for all 2-3-4-5 way combinations of these categories:
```{r echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   #load weicheng's correlation matrix:
   #need catcor, catmat
   #setwd("../weicheng/"); source("./categoryExploration.R"); setwd("../ian/");

   #get counts of times any tow catIDs are seen together by column
   catmat = data.frame(cbind(splitCats[,c(1,15,17:21)], matrix(sapply(1:nrow(splitCats), function(i) as.numeric(paste0("cat",1:31) %in% splitCats[i,17:21])),byrow=TRUE,nrow=nrow(splitCats))))[,-(3:7)] %>% 
      renm(c("orderID","couponCol",paste0("cat",1:31))) 
   catID = catmat %>%  
      mutate(nCats = rowSums(catmat[,3:33])) %>%
      gather(catID,incpn,-couponCol,-orderID,-nCats) %>% 
      filter(incpn == 1) 
   catID = catID %>% 
      mutate(catIDnum = as.numeric(gsub('cat','',as.character(catID$catID)))) %>% 
      arrange(orderID,couponCol,catIDnum)

   catID1 = catID[which(catID$nCats >= 1),] %>% renm(c("orderID","couponCol","nCats","catID1","incpn","catID1num"))
   catID2 = catID[which(catID$nCats >= 2),] %>% renm(c("orderID","couponCol","nCats","catID2","incpn","catID2num")) %>% left_join(catID1[which(catID1$nCats > 1),],by=c("orderID","couponCol","nCats","incpn")) %>% filter(catID1num < catID2num)
   catID3 = catID[which(catID$nCats >= 3),] %>% renm(c("orderID","couponCol","nCats","catID3","incpn","catID3num")) %>% left_join(catID2[which(catID2$nCats > 2),],by=c("orderID","couponCol","nCats","incpn")) %>% filter(catID2num < catID3num)
   catID4 = catID[which(catID$nCats >= 4),] %>% renm(c("orderID","couponCol","nCats","catID4","incpn","catID4num")) %>% left_join(catID3[which(catID3$nCats > 3),],by=c("orderID","couponCol","nCats","incpn")) %>% filter(catID3num < catID4num)
   catID5 = catID[which(catID$nCats >= 5),] %>% renm(c("orderID","couponCol","nCats","catID5","incpn","catID5num")) %>% left_join(catID4[which(catID4$nCats > 4),],by=c("orderID","couponCol","nCats","incpn")) %>% filter(catID4num < catID5num) 

   catID2 = catID1 %>% mutate(catID2num = NA, catID2 = NA) %>% rbind(catID2)
   catID3 = catID2 %>% mutate(catID3num = NA, catID3 = NA) %>% rbind(catID3)
   catID4 = catID3 %>% mutate(catID4num = NA, catID4 = NA) %>% rbind(catID4)
   catID5 = catID4 %>% mutate(catID5num = NA, catID5 = NA) %>% rbind(catID5) %>% arrange(orderID,couponCol,catID5num,catID4num,catID3num,catID2num,catID1num)

   catCombFreq = catID5 %>% 
      group_by(catID1,catID2,catID3,catID4,catID5,couponCol) %>% 
      summarize(nCatCount = sum(incpn)) %>% 
      arrange(catID1, catID2, catID3, catID4, catID5) %>% 
      spread(couponCol,nCatCount) %>% 
      renm(c(paste0("catID",1:5),paste0("nCatXcol",1:3))) %>% 
      mutate(nCatXtotal = nCatXcol1 + nCatXcol2 + nCatXcol3) %>%
      gather(varname,value,-catID1,-catID2,-catID3,-catID4,-catID5)
   catCombFreq$value[which(is.na(catCombFreq$value))] = 0
```

```{r echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   catmatTR = data.frame(cbind(split.trn[,c(1,14:20)], matrix(sapply(1:nrow(split.trn), function(i) as.numeric(paste0("cat",1:31) %in% split.trn[i,16:20])),byrow=TRUE,nrow=nrow(split.trn))))[,-(4:8)] %>% renm(c("orderID","couponUsed","couponCol",paste0("cat",1:31))) 
   catIDTR = catmatTR %>%  
      mutate(nCats = rowSums(catmatTR[,4:34])) %>%
      gather(catID,incpn,-couponCol,-orderID,-nCats,-couponUsed) %>% 
      filter(incpn == 1) 
   catIDTR = catIDTR %>% 
      mutate(catIDnum = as.numeric(gsub('cat','',as.character(catIDTR$catID)))) %>% 
      arrange(orderID,couponCol,catIDnum)

   catIDTR1 = catIDTR[which(catIDTR$nCats >= 1),] %>% renm(c("orderID","couponUsed","couponCol","nCats","catID1","incpn","catID1num"))
   catIDTR2 = catIDTR[which(catIDTR$nCats >= 2),] %>% renm(c("orderID","couponUsed","couponCol","nCats","catID2","incpn","catID2num")) %>% left_join(catIDTR1[which(catIDTR1$nCats > 1),],by=c("orderID","couponUsed","couponCol","nCats","incpn")) %>% filter(catID1num < catID2num)
   catIDTR3 = catIDTR[which(catIDTR$nCats >= 3),] %>% renm(c("orderID","couponUsed","couponCol","nCats","catID3","incpn","catID3num")) %>% left_join(catIDTR2[which(catIDTR2$nCats > 2),],by=c("orderID","couponUsed","couponCol","nCats","incpn")) %>% filter(catID2num < catID3num)
   catIDTR4 = catIDTR[which(catIDTR$nCats >= 4),] %>% renm(c("orderID","couponUsed","couponCol","nCats","catID4","incpn","catID4num")) %>% left_join(catIDTR3[which(catIDTR3$nCats > 3),],by=c("orderID","couponUsed","couponCol","nCats","incpn")) %>% filter(catID3num < catID4num)
   catIDTR5 = catIDTR[which(catIDTR$nCats >= 5),] %>% renm(c("orderID","couponUsed","couponCol","nCats","catID5","incpn","catID5num")) %>% left_join(catIDTR4[which(catIDTR4$nCats > 4),],by=c("orderID","couponUsed","couponCol","nCats","incpn")) %>% filter(catID4num < catID5num) 

   catIDTR2 = catIDTR1 %>% mutate(catID2num = NA, catID2 = NA) %>% rbind(catIDTR2)
   catIDTR3 = catIDTR2 %>% mutate(catID3num = NA, catID3 = NA) %>% rbind(catIDTR3)
   catIDTR4 = catIDTR3 %>% mutate(catID4num = NA, catID4 = NA) %>% rbind(catIDTR4)
   catIDTR5 = catIDTR4 %>% mutate(catID5num = NA, catID5 = NA) %>% rbind(catIDTR5) %>% arrange(orderID,couponCol,catID5num,catID4num,catID3num,catID2num,catID1num)

   catCombFreqTR = catIDTR5 %>% 
      group_by(catID1,catID2,catID3,catID4,catID5,couponCol,couponUsed) %>% 
      summarize(nCatCount = sum(incpn)) %>% 
      arrange(catID1, catID2, catID3, catID4, catID5) %>% 
      spread(couponCol,nCatCount) %>% 
      renm(c(paste0("catID",1:5),"couponUsed",paste0("propCatUsedXcol",1:3))) %>% 
      mutate(propCatUsedTotal = propCatUsedXcol1 + propCatUsedXcol2 + propCatUsedXcol3) %>%
      gather(couponCol, count, -catID1, -catID2, -catID3, -catID4, -catID5, -couponUsed) %>%
      spread(couponUsed,count) %>%
      renm(c(paste0("catID",1:5),"couponCol",paste0("used",0:1))) 
   catCombFreqTR$used0[which(is.na(catCombFreqTR$used0))] = 0
   catCombFreqTR$used1[which(is.na(catCombFreqTR$used1))] = 0
   catCombFreqTR = catCombFreqTR %>% mutate(value = used1/(used0 + used1)) 
   catCombFreqTR = catCombFreqTR[,-which(names(catCombFreqTR) %in% c("used0","used1"))] %>% spread(couponCol,value)

   catCombFreq = catCombFreqTR %>% 
      gather(varname,value,-catID1,-catID2,-catID3,-catID4,-catID5) %>% 
      rbind(catCombFreq) %>% 
      spread(varname,value) %>% 
      data.frame

   #There are some missing values in this use frequenct matrix (this is to be expected) I can impute the values using missForest
   impute.missing1000 = missForest(catCombFreq[,6:ncol(catCombFreq)], maxiter=10, ntree = 1000, verbose =TRUE, mtry = 5, replace = TRUE)

   catCombFreq = catCombFreq[,1:5] %>% cbind(impute.missing1000$ximp)
```
We now have two valuable tools: \verb!catFreq! and \verb!catCombFreq!
I will save these to a my written directory folder:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   saveRDS(catCombFreq,'./written_data/catCombFreq.rds')
   saveRDS(catFreq,'./written_data/catFreq.rds')
```


<!--- 
```{r corrplot,echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}

   #get counts of times any two catIDs are seen together
   countMat = matrix(0,3*31,32)
   for(i in 1:3){
      for(j in 1:31){ 
         for (k in (j+1):31){ 
            row.j = (i-1)*31 + j
            countMat[row.j,k] = sum(catmat[which(catmat[,32] == i),j]*catmat[which(catmat[,32] == i),k]) 
         } 
         countMat[row.j,32] = i
      }
   }

   countData = as.data.frame(countMat)
   names(countData) = c(paste0("cat",1:31),'couponCol')
   countData$cols = rep(names(countData)[1:31],3)

   countData = countData %>% 
      gather(catID2,prop,-cols,-couponCol) %>%  
      arrange(cols,catID2) %>% 
      renm(c("couponCol","catID1","catID2","nTotal")) %>% 
      unique %>% 
      spread(couponCol,nTotal) %>%
      renm(c("catID1","catID2","nTotalCol1","nTotalCol2","nTotalCol3"))
```
We now have a matrix identifying correlation between two categories and the number of times they occur.

We can get correlation matrix and count matrix for when coupons are being used as well:
```{r echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
#   #get counts of times any tow catIDs are seen together IN THE TRAINING SET
#   catmatTR = matrix(0,nrow(split.trn),32)
#   for(i in 1:nrow(catmatTR)){
#      catmatTR[i,1:31] = as.numeric(paste0("cat",1:31) %in% split.trn[i,16:20])
#      catmatTR[i,32] = split.trn$couponCol[i]
#   }
#
#   pcorrmatTR = cor(catmatTR[,1:31])
#
#   #get counts of times any tow catIDs are seen together IN THE TRAINING SET
#   countMatTR = matrix(0,3*31,32)
#   for(i in 1:3){
#      for(j in 1:31){ 
#         for (k in (j+1):31){ 
#            row.j = (i-1)*31 + j
#            countMatTR[row.j,k] = sum(catmatTR[which(catmatTR[,32] == i),j]*catmatTR[which(catmatTR[,32] == i),k]) 
#         } 
#         countMatTR[row.j,32] = i
#      }
#   }
#
#   countDataTR = as.data.frame(countMatTR)
#   names(countDataTR) = c(paste0("cat",1:31),'couponCol')
#   countDataTR$cols = rep(names(countDataTR)[1:31],3)
#
#   countDataTR = countDataTR %>% 
#      gather(catID2,prop,-cols,-couponCol) %>%  
#      arrange(cols,catID2) %>% 
#      renm(c("couponCol","catID1","catID2","nTotal")) %>% 
#      unique %>% 
#      spread(couponCol,nTotal) %>%
#      renm(c("catID1","catID2","nTotalCol1","nTotalCol2","nTotalCol3"))
#
#
#   #do the same for when coupons are used
#   splitCatsUsedTR = split.trn[which(split.trn$couponUsed == 1),]
#
#   #get counts of times any tow catIDs are seen together IN THE UsedTRAINING SET
#   catmatUsedTR = matrix(0,nrow(splitCatsUsedTR),32)
#   for(i in 1:nrow(catmatUsedTR)){
#      catmatUsedTR[i,1:31] = as.numeric(paste0("cat",1:31) %in% splitCatsUsedTR[i,16:20])
#      catmatUsedTR[i,32] = splitCatsUsedTR$couponCol[i]
#   }
#
#   pcorrmatUsedTR = cor(catmatUsedTR[,1:31])
#
#   #get counts of times any tow catIDs are seen together IN THE UsedTRAINING SET
#   countMatUsedTR = matrix(0,3*31,32)
#   for(i in 1:3){
#      for(j in 1:31){ 
#         for (k in (j+1):31){ 
#            row.j = (i-1)*31 + j
#            countMatUsedTR[row.j,k] = sum(catmatUsedTR[which(catmatUsedTR[,32] == i),j]*catmatUsedTR[which(catmatUsedTR[,32] == i),k]) 
#         } 
#         countMatUsedTR[row.j,32] = i
#      }
#   }
#
#   countUsedData = as.data.frame(countMatUsedTR)
#   names(countUsedData) = c(paste0("cat",1:31),'couponCol')
#   countUsedData$cols = rep(names(countUsedData)[1:31],3)
#
#   countUsedData = countUsedData %>% 
#      gather(catID2,propUsed,-cols,-couponCol) %>%  
#      arrange(cols,catID2) %>% 
#      renm(c("couponCol","catID1","catID2","nUsed")) %>% 
#      unique %>% 
#      spread(couponCol,nUsed) %>%
#      renm(c("catID1","catID2","nUsedCol1","nUsedCol2","nUsedCol3"))
#
#   countDataTR$nTotal = with(countDataTR,nTotalCol1 + nTotalCol2 + nTotalCol3)
#   countUsedData$nUsed = with(countUsedData,nUsedCol1 + nUsedCol2 + nUsedCol3)
#
#   propTable = countDataTR %>% full_join(countUsedData,by=c("catID1","catID2"))
#
#   propTable$propUsedCol1 = with(propTable,nUsedCol1/nTotalCol1)
#   propTable$propUsedCol2 = with(propTable,nUsedCol2/nTotalCol2)
#   propTable$propUsedCol3 = with(propTable,nUsedCol3/nTotalCol3)
#   propTable$propUsed = with(propTable,nUsed/nTotal)
#
#   countData$nTotal = with(countData,nTotalCol1 + nTotalCol2 + nTotalCol3)
#
#   dogFreq = countData %>% full_join(propTable[,c("catID1","catID2","propUsedCol1", "propUsedCol2", "propUsedCol3", "propUsed")],by=c("catID1","catID2"))
#   dogFreq = dogFreq %>% filter(nTotal > 0)
#
#   qplot(catID1,catID2,color=nTotal,size=propUsed,data=dogFreq)
```

We can save this output:
```{r echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
#   saveRDS(catFreq,file="../features/feature_files/one-way_categoricalProportions.rds")
#   saveRDS(dogFreq,file="../features/feature_files/two-way_categoricalProportions.rds")
```
-->
