---
title: Exploring basePrice and Price
titleshort: basePrice/Price
instructions:
author: Chen Hua, Ian Mouzon
authorshort: Hua/Mouzon
contact: chua@iastate.edu, imouzon@iastate.edu
grouplong: Iowa State University's 2015 Data Mining Cup Team
groupshort: DMC@ISU
leader: One Week Left 
leadershort: One Week Left
semester: Spring 2015
assignment: 
duedate: May 8, 2015
output:
  usefulR::hw_format:
  keep_tex: true
---

<!--- # (R code (No Results in Document)) -->
```{r set-parent, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   #set up knitr
   #devtools::install_github('imouzon/usefulR')
   library(usefulR)

   #set working directory
   working.dir = "~/dmc2015/ian"
   setwd(working.dir)

   #compile the document to PDF
   if(FALSE) 
      rmarkdown::render("./categorical_similarity.Rmd")
```
I am using the following packages:
<!--- # (R code (No Results in Document))-->
```{r paks, echo=TRUE, cache=FALSE, message=FALSE, tidy=FALSE, include=TRUE}
   library(ggplot2)
   library(lubridate)
   library(xtable)
   library(foreach)
   library(rCharts)
   library(magrittr)
   library(tidyr)
   library(dplyr)
   library(reshape2)
   library(gtools)
   library(sqldf)
   library(missForest)
   source("./R/renm.R")
```
and our working directory is set to \verb!dmc2015/ian!.

# price and basePrice - What Can We Do With Them???

# Getting the Data and Manipulations 
I am using our new clean data - so should you
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
   d = readRDS("../data/clean_data/universalCleanData.rds")
```

I can melt the columns by coupon using the following:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   source("./r/stackCoupons2.R")
   dm = stackCoupons2(d,idcols = c(1:4,32:49))
```

I and can split the columns of product group using:
<!--- splitcols: R code (No Results in Document) -->
```{r splitcols,cache=FALSE}
   source("./r/splitColumn.R")
   dmc = splitColumn(dm,"categoryIDs","orderID",splitby=":") 
```

<!--- chensCod: R code (No Results in Document) -->
```{r chensCod,cache=FALSE}
   ########  ------  Counting number of sub-category IDs  ------  ########
   countCat = function(dat){
     df = as.data.frame(5 - apply(dat, 1, function(vec) sum(is.na(vec))))
     colnames(df) = "nSubCats"
     return(df)
   }


   dmc = 
   item_choose = "brand1 prod1 cat1:cat2"
   dmc %>% filter(item_key==item_choose) %>% select(couponID,price) %>% unique %>% mutate(
   %>%
      summarize(price_level=unique(price)) 
   %>% 
      select(price_level) 
      %>%
      unique


   function(dsn,item_choose){
      dsn %>% filter(item_key == item_choose)  
      
   head(dmc)
   qplot(item_key,reward,data=dmc)
   length(unique(dmc$couponID))
   dmc$item_key = paste(b
   nrow(unique(dmc[,c("brand","productGroup","categoryIDs")]))
   ,"premiumProduct"
   



   p = readRDS("../chen/datClean2.rds")
   p = d 


   linegroup = d %>% mutate(linegrp = as.factor(price/basePrice))  
   linegroup %>% group_by(linegrp) %>% summarize(freq = n()) %>% arrange(-freq)

   chk = linegroup[which(linegroup$linegrp == "4.99397590361446"),]
   chk %>% select(couponID,brand,productGroup,reward) %>% unique %>% arrange(brand,productGroup)

   d[which(d$couponID %in% c("cpn2146","cpn3274","cpn339")),]

   qplot(log(price),log(basePrice),color=linegrp,data=chk) + theme(legend.position="none")

   levels(linegroup$linegrp)


   qplot(log(price),log(basePrice),data=p)

   qplot(as.character(price/(basePrice)^(1.1)),couponID,data=d)

   qplot(price,basePrice,data=p)
   qplot(price,log(basePrice),data=p)
   qplot(log(price),log(basePrice),data=p)




   p = as.data.frame(p)

   iplot(log(p$price),log(p$basePrice))
   ihist(log(p$price))

   qplot(log(price),log(basePrice),color=as.factor(couponUsed),data=p)

   p %>% filter(brand=="brand3") %>% ggplot(aes(x=log(price),y=log(basePrice),color=factor(couponUsed),alpha=.01)) + geom_point() + facet_grid(couponUsed~.) + theme(legend.position="bottom")

   p %>% filter(brand=="brand3") %>% ggplot(aes(x=log(price),y=log(basePrice),color=factor(couponUsed),alpha=.01)) + geom_point() + theme(legend.position="bottom")
```

## Kernal Mechanics

Using the kernal function: $K(\mathbf{x}, \mathbf{y}) = \left(\alpha + \langle \mathbf{x}, \mathbf{y} \rangle \right)^{\eta}$:
<!--- kernalMechanics: R code (No Results in Document) -->
```{r kernalMechanics,cache=FALSE}
   Kst = function(x,y,alpha=0,eta=1){
      alpha=0
      eta=1
      x = log(K.d$price)
      y = log(K.d$basePrice)
      K = matrix(c(x,y),nrow=length(x),byrow=FALSE)

      #center
      K = t(t(K) - colMeans(K))

      #apply kernal function
      Kmat = (alpha + K%*%t(K))^eta

      return(Kmat)
   }
```
We apply this kernal:
<!--- applyKernal: R code (No Results in Document) -->
```{r applyKernal,cache=FALSE}
   K.d = unique(d[!(d$basePrice == 0),c(3:4)])

   K01 = Kst(log(K.d$price),log(K.d$basePrice))
   K11 = Kst(log(K.d$price),log(K.d$basePrice),alpha=1)
   K12 = Kst(log(K.d$price),log(K.d$basePrice),alpha=1,eta=2)

   plot_func = function(i,kernalmat=K01){
      Kplot2 = K.d[i,]
      K.plot = cbind(K.d,kernalmat[,i])
      names(K.plot)[3] = "kernaltransform"
      p = ggplot(data = K.plot, aes(x = log(price), y=log(basePrice), color= kernaltransform)) + 
      geom_point() +
      geom_point(data=Kplot2,aes(x=log(price),y=log(basePrice)),shape=3,color='orange') + 
      geom_vline(xintercept=mean(log(K.d$price))) + 
      geom_hline(yintercept=mean(log(K.d$basePrice)))
      print(p)
   }
```

<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
plot_func(120,Kst(log(K.d$price,log(K.d$basePrice),alpha=2,eta=4)))
   
      dogs = function(i,type='prod'){
         varn = paste0(type,i)
         p = d %>% filter(brand == varn) %>% unique

         p = ggplot(data=K.d,aes(x = log(price), y=log(basePrice))) + 
             geom_point() +
             geom_point(data=p,aes(x = log(price),y=log(basePrice)),color='red') 
         print(p)
      }
      
```

   <!--- chunk-label: R code (No Results in Document) -->
   ```{r chunk-label,cache=FALSE}
   
      dogs(3)
      dogs(13)
      sapply(1:40, function(x) print(dogs(x,"brand")))

      + 
      geom_point() +
      geom_point(data=Kplot2,aes(x=log(price),y=log(basePrice)),shape=3,color='orange') + 
      geom_vline(xintercept=mean(log(K.d$price))) + 
      geom_hline(yintercept=mean(log(K.d$basePrice)))
      print(p)
   }
```





   
<!--- R code (No Results in Document) -->
```{r cache=FALSE}
   

   nlevels(as.factor(d$price))
   nlevels(as.factor(d$basePrice))
   nlevels(as.factor(d$reward))

   mylist = c("orderID", "couponID", "price", "basePrice", "reward", "premiumProduct",
              "brand", "productGroup", "catSub1", "catSub2","catSub3","catSub4","catSub5", "couponUsed", "basketValue")
   mydat <- d[ , mylist]
# saveRDS(mydat, file = "datClean2.rds")
   mydat = readRDS("datClean2.rds")

   nSubCats <- countCat(mydat[,9:13])
   mydat = cbind(mydat, nCatSubs)


   z1 <- mydat[mydat$nSubCats == 1 ,]
   z2 <- mydat[mydat$nSubCats == 2 ,]
   z3 <- mydat[mydat$nSubCats == 3 ,]
   z4 <- mydat[mydat$nSubCats == 4 ,]
   z5 <- mydat[mydat$nSubCats == 5 ,]
    
   prodInfo = unique(mydat[,c("couponID", "price", "basePrice", "reward", "brand", "productGroup",
            "catSub1", "catSub2",	"catSub3", "catSub4",	"catSub5","nSubCats")]) %>% arrange(-nSubCats,brand,reward)
   prodInfo.order = prodInfo[order(prodInfo$nSubCats), ]

   count(prodInfo$brand)




# 22.6% of products are premium products
   nrow(mydat[mydat$premiumProduct == 1,])/nrow(mydat)
   nrow(mydat[mydat$premiumProduct == 0,])

   levels(as.factor(mydat[mydat$premiumProduct==1,]$reward))
   nlevels(as.factor(mydat[mydat$premiumProduct==0,]$reward))

   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 0,])
   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 0.63,])
   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 0.94,])
   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 1.26,])
   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 1.57,])
   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 1.88,])
   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 2.2,])
   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 2.51,])
   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 3.14,])
   nrow(mydat[mydat$premiumProduct==1 & mydat$reward == 6.28,])

   z <- mydat[mydat$premiumProduct==1 & mydat$reward == 1.26,]




   hist(mydat[mydat$premiumProduct==1 & mydat$reward == 1.26,]$price)
   hist(mydat[mydat$premiumProduct==1 & mydat$reward == 1.26 & mydat$basePrice > 30, ]$basePrice)
   range(mydat[mydat$premiumProduct==1 & mydat$reward == 1.26, ]$basePrice)

   hist(mydat[mydat$premiumProduct==1 & mydat$reward == 1.26 & mydat$basePrice > 10, ]$basePrice)

   mydat[mydat$premiumProduct==1 & mydat$reward == 1.26 & mydat$basePrice > 10,]

   nrow(mydat[mydat$basePrice == 324.17, ])

   mydat[mydat$premiumProduct==1, ]$basePrice


   mydat[mydat$premiumProduct==1 & mydat$reward == 1.26 & mydat$brand %in% "brand1", ]
   d[d$premiumProduct==1 & d$reward == 1.26 & d$brand %in% "brand3", ]
# d[d$premiumProduct==1 & d$reward == 1.26 & d$brand %in% "brand4", ]
   d[d$premiumProduct==1 & d$reward == 1.26 & d$brand %in% "brand5", ]
   d[d$premiumProduct==1 & d$reward == 1.26 & d$brand %in% "brand16", ]
   d[d$premiumProduct==1 & d$reward == 1.26 & d$brand %in% "brand17", ]
   d[d$premiumProduct==1 & d$reward == 1.26 & d$brand %in% "brand18", ]
   d[d$premiumProduct==1 & d$reward == 1.26 & d$brand %in% "brand20", ]
   d[d$premiumProduct==1 & d$reward == 1.26 & d$brand %in% "brand23", ]

   brand1
   brand3
   brand4
   brand5
   brand16
   brand17
   brand18
   brand20
   brand23


   z <- d[d$premiumProduct==1 & d$reward == 1.26 & d$brand %in% "brand4", ]



      
```


