---
title: Cory's LLR Statistics
titleshort: Cory's LLR
instructions:
author: Pete Walsh and Ian Mouzon
authorshort: imouzon
contact: imouzon@iastate.edu
grouplong: Data Mining Cup 2015 
groupshort: DMC2015
leader: Iowa State University Data Mining Cup Team
leadershort: DMC2015@ISU
semester: Spring 2015
assignment: 
duedate: May 6, 2015
output:
  usefulR::hw_format
---

<!--- # (R code (No Results in Document)) -->
```{r set-parent, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   #set up knitr
   #devtools::install_github('imouzon/usefulR')
   library(usefulR)

   #set working directory
   working.dir = '~/dmc2015/ian/'
   setwd(working.dir)

   #compile the document to PDF
   if(FALSE) 
      rmarkdown::render("~/dmc2015/ian/CorysLLR.rmd")
```

I am using the following pacakges:
<!--- # (R code (No Results in Document))-->
```{r paks, echo=TRUE, cache=TRUE, message=FALSE, tidy=FALSE, include=TRUE}
   library(ggplot2)
   library(lubridate)
   library(xtable)
   library(foreach)
   library(rCharts)
   library(magrittr)
   library(tidyr)
   library(dplyr)
   library(reshape2)
   library(gtools)
   library(sqldf)
   library(missForest)
   source("~/dmc2015/ian/R/renm.R")
```
and my working directory is set to \verb!dmc2015/ian!.

# Pete's LLR Code
Pete has written some wonderful functions to compute One-way and Two-Way loglikelihood estimates based on the historical data.
I am recopying them here for preservation.
<!--- chunk-label: R code (No Results in Document) -->
```{r PetesFunc1,cache=TRUE}
   # Code to compute estimated log-likelihood ratios for categorical 
   # variables and binary response. The second function is to calculate the 
   # log-likelihood ratios for an interaction between two categorical variables.
   # This is based on the work by Cory Lanker.
   #
   # If you want to understand exactly what the code below is doing, I 
   # recommend running the code within the functions step-by-step using the 
   # examples that I created below each function. Let me know if you have any
   # questions. The justification for this approach is explained in Cory Lanker's
   # thesis paper.

   compute_ll <- function(x, y, targetX, epsilon1 = NULL, epsilon2 = NULL)  {
     # x A character vector
     # y A numeric vector of 0's and 1's
     # targetX A character vector with the same categories as x
     # Takes a categorical predictor variable, x, and a binary response
     # variable, y, and produces a vector of the estimated log-likelihood
     # statistics for the targetX column. An epsilon > 0 is added to the numerator 
     # and denominator to prevent numerical instability.
     # Non-matching categories will result in NA entries
     stopifnot(all(y %in% c(0,1))) # response has to be binary
     if (is.null(epsilon1) | is.null(epsilon2)) {
       epsilon1 = mean(y)
       epsilon2 = 1 - epsilon1
     }
     levs <- unique(x)
     # This will create a vector of the estimated log-likelihood ratios for
     # each level of the explanatory variable. 
     lls <- sapply(levs, FUN = function(levs) {
                     log((sum(x == levs & y == 1) + epsilon1) / 
                         (sum(x == levs & y == 0) + epsilon2))
                   })
     res <- lls[targetX]
     names(res) <- targetX
     res[is.na(res)] <- log(epsilon1 / epsilon2)
     return(res)
   }

   compute_ll_2w <- function(x1, x2, y, targetX1, targetX2, 
                             epsilon1 = NULL,
                             epsilon2 = NULL) {
     # x1 A character vector
     # x2 A character vector
     # y A numeric vector of 0's and 1's
     # targetX1 A character vector with the same categories as x1
     # targetX2 A character vector with the same categories as x2
     # Takes 2 categorical predictor variables, x1 and x2, and a binary response
     # variable, y, and produces a vector of the estimated log-likelihood
     # statistics for all combinations between the levels of each predictor for
     # targetX1 and targetX2.
     # An epsilon > 0 is added to the numerator and denominator to prevent 
     # numerical instability.
     # Non-matching categories will result in NA entries
     stopifnot(all(y %in% c(0,1))) # response has to be binary
     if (is.null(epsilon1) | is.null(epsilon2)) {
       epsilon1 = mean(y)
       epsilon2 = 1 - epsilon1
     }
     levs_1 <- unique(x1)
     levs_2 <- unique(x2)
     # Using sapply within sapply will create a matrix. This will create a matrix 
     # of the estimated log-likelihood ratios for each unique combination of the 
     # levels of each explanatory variable.
     lls <- sapply(levs_2, FUN = function(levs_2) {
                     sapply(levs_1, FUN = function(levs_1) {
                              log((sum(x1 == levs_1 & x2 == levs_2 & y == 1) + epsilon1) / 
                                  (sum(x1 == levs_1 & x2 == levs_2 & y == 0) + epsilon2))
                            })
                   })
     index <- 1:length(targetX1)
     res <- sapply(index, FUN = function(index) {
                     if (targetX1[index] %in% rownames(lls) & 
                         targetX2[index] %in% colnames(lls)) {
                       lls[targetX1[index], targetX2[index]]
                     } else {
                       NA
                     }
                   })
     res[is.na(res)] <- log(epsilon1 / epsilon2)
     return(res)
   }
```

#Reading the data into R
<!--- chunk-label: R code (No Results in Document) -->
```{r readingInTheData,cache=TRUE}
   #clean data
   d = readRDS("~/dmc2015/data/clean_data/clean_simple.rds")
   S1 = readRDS("~/dmc2015/data/featureMatrix/HTVset1.rds")
   S2 = readRDS("~/dmc2015/data/featureMatrix/HTVset2.rds")
   S3 = readRDS("~/dmc2015/data/featureMatrix/HTVset3.rds")
```
and we need to manipulate the variables so that we have couponID in the key and
the order status as the primary response.
<!--- cpn1way: R code (No Results in Document) -->
```{r cpn1way,cache=TRUE}
   source("./R/stackCoupons.R")

   TV = stackCoupons(S1$T,S1$V,nms=c("train","validation"))
   TC = stackCoupons(S1$T,S1$C,nms=c("train","class"))

   trn = TV$combined %>% filter(dsn == "train")
   val = TV$combined %>% filter(dsn == "validation")
   cls = TC$combined %>% filter(dsn == "class")

   TVC = trn %>% rbind(val) %>% rbind(cls)

   H = stackCoupons(S1$T,S1$H,nms=c("train","historical"))$combined %>%
      filter(dsn == "historical")
```
Occasionally, there are issues with factor conversion. 
To avoid this, I am converting the following values to characters:
<!--- fact2char: R code (No Results in Document) -->
```{r fact2charTV,cache=TRUE}
   TVC$userID = as.character(TVC$userID)

   TVC$couponID = as.character(TVC$couponID)
      TVC$categoryIDs = as.character(TVC$categoryIDs)
      TVC$reward = as.character(TVC$reward)
      TVC$brand = as.character(TVC$brand)
      TVC$productGroup = as.character(TVC$productGroup)
      TVC$premiumProduct = as.character(TVC$premiumProduct)
      TVC$couponCol = as.character(TVC$couponCol)
```
And we do the same for the historical data
<!--- fact2char: R code (No Results in Document) -->
```{r fact2char,cache=TRUE}
   H$userID = as.character(H$userID)

   H$couponID = as.character(H$couponID)
      H$categoryIDs = as.character(H$categoryIDs)
      H$reward = as.character(H$reward)
      H$brand = as.character(H$brand)
      H$productGroup = as.character(H$productGroup)
      H$premiumProduct = as.character(H$premiumProduct)
      H$couponCol = as.character(H$couponCol)
```

   
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE, include=FALSE}
   #chk = H %>% group_by(couponID) %>% summarize(count = n(), nUsed = sum(couponUsed)) %>% arrange(-count) %>% with(table(count,nUsed)) %>% data.frame
   #qplot(count,nUsed,data=chk,size=Freq)
```
   

# Calculating Coupon 1-Way Likelihoods

## Raw Data Variables
*userID*
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE}
   # userID
   llr = compute_ll(as.character(H$userID),H$couponUsed,as.character(TVC$userID))
   llr_userID = data.frame("userID" = names(llr), "llr_userID" = llr) %>% arrange(userID) %>% unique

   #plot the results
   if(nrow(TVC) - sum(TVC$userID %in% llr_userID$userID)) warning("Things aren't adding up")
   qplot(as.numeric(gsub("user","",userID)), llr_userID,data=llr_userID)

   #Isolate the features
   llr_userID_long = TVC %>% 
      left_join(llr_userID,by="userID") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_userID) 

   trn = llr_userID_long %>% filter(dsn == "train") %>% select(orderID,couponCol,llr_userID) 
   val = llr_userID_long %>% filter(dsn == "validation") %>% select(orderID,couponCol,llr_userID) 
   cls = llr_userID_long %>% filter(dsn == "class") %>% select(orderID,couponCol,llr_userID) 

   llr_userID_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userID_long,"../features/feature_files/llr_userID_long_set1.rds")

   #save the results to RDS in WIDE format
   llr_userID_wide = TVC %>% left_join(llr_userID,by="userID") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_userID) %>% 
      spread(couponCol,llr_userID) %>% 
      renm(c("orderID","dsn", "llr_userID1", "llr_userID2", "llr_userID3")) 

   trn = llr_userID_wide %>% filter(dsn == "train") %>% select(orderID,llr_userID1,llr_userID2,llr_userID3) 
   val = llr_userID_wide %>% filter(dsn == "validation") %>% select(orderID,llr_userID1,llr_userID2,llr_userID3) 
   cls = llr_userID_wide %>% filter(dsn == "class") %>% select(orderID,llr_userID1,llr_userID2,llr_userID3) 

   llr_userID_wide = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userID_wide,"../features/feature_files/llr_userID_wide_set1.rds")
```


*couponID*
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE}
   # couponID
   llr = compute_ll(as.character(H$couponID),H$couponUsed,as.character(TVC$couponID))
   llr_couponID = data.frame("couponID" = names(llr), "llr_couponID" = llr) %>% arrange(couponID) %>% unique

   #plot the results
   if(nrow(TVC) - sum(TVC$couponID %in% llr_couponID$couponID)) warning("Things aren't adding up")
   qplot(as.numeric(gsub("cpn","",couponID)), llr_couponID,data=llr_couponID)

   #Isolate the features
   llr_couponID_long = TVC %>% 
      left_join(llr_couponID,by="couponID") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_couponID) 

   trn = llr_couponID_long %>% filter(dsn == "train") %>% select(orderID,couponCol,llr_couponID) 
   val = llr_couponID_long %>% filter(dsn == "validation") %>% select(orderID,couponCol,llr_couponID) 
   cls = llr_couponID_long %>% filter(dsn == "class") %>% select(orderID,couponCol,llr_couponID) 

   llr_couponID_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_couponID_long,"../features/feature_files/llr_couponID_long_set1.rds")

   #save the results to RDS in WIDE format
   llr_couponID_wide = TVC %>% left_join(llr_couponID,by="couponID") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_couponID) %>% 
      spread(couponCol,llr_couponID) %>% 
      renm(c("orderID","dsn", "llr_couponID1", "llr_couponID2", "llr_couponID3")) 

   trn = llr_couponID_wide %>% filter(dsn == "train") %>% select(orderID,llr_couponID1,llr_couponID2,llr_couponID3) 
   val = llr_couponID_wide %>% filter(dsn == "validation") %>% select(orderID,llr_couponID1,llr_couponID2,llr_couponID3) 
   cls = llr_couponID_wide %>% filter(dsn == "class") %>% select(orderID,llr_couponID1,llr_couponID2,llr_couponID3) 

   llr_couponID_wide = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_couponID_wide,"../features/feature_files/llr_couponID_wide_set1.rds")
```

*reward*
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE}
   # reward
   llr = compute_ll(as.character(H$reward),H$couponUsed,as.character(TVC$reward))
   llr_reward = data.frame("reward" = names(llr), "llr_reward" = llr) %>% arrange(reward) %>% unique

   #plot the results
   if(nrow(TVC) - sum(TVC$reward %in% llr_reward$reward)) warning("Things aren't adding up")
   qplot(reward, llr_reward,data=llr_reward)

   #Isolate the features
   llr_reward_long = TVC %>% 
      left_join(llr_reward,by="reward") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_reward) 

   trn = llr_reward_long %>% filter(dsn == "train") %>% select(orderID,couponCol,llr_reward) 
   val = llr_reward_long %>% filter(dsn == "validation") %>% select(orderID,couponCol,llr_reward) 
   cls = llr_reward_long %>% filter(dsn == "class") %>% select(orderID,couponCol,llr_reward) 

   llr_reward_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_reward_long,"../features/feature_files/llr_reward_long_set1.rds")

   #save the results to RDS in WIDE format
   llr_reward_wide = TVC %>% left_join(llr_reward,by="reward") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_reward) %>% 
      spread(couponCol,llr_reward) %>% 
      renm(c("orderID","dsn", "llr_reward1", "llr_reward2", "llr_reward3")) 

   trn = llr_reward_wide %>% filter(dsn == "train") %>% select(orderID,llr_reward1,llr_reward2,llr_reward3) 
   val = llr_reward_wide %>% filter(dsn == "validation") %>% select(orderID,llr_reward1,llr_reward2,llr_reward3) 
   cls = llr_reward_wide %>% filter(dsn == "class") %>% select(orderID,llr_reward1,llr_reward2,llr_reward3) 

   llr_reward_wide = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_reward_wide,"../features/feature_files/llr_reward_wide_set1.rds")
```

*brand*
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE}
   # brand
   llr = compute_ll(as.character(H$brand),H$couponUsed,as.character(TVC$brand))
   llr_brand = data.frame("brand" = names(llr), "llr_brand" = llr) %>% arrange(brand) %>% unique

   #plot the results
   if(nrow(TVC) - sum(TVC$brand %in% llr_brand$brand)) warning("Things aren't adding up")
   qplot(as.numeric(gsub("brand","",brand)), llr_brand,data=llr_brand)

   #Isolate the features
   llr_brand_long = TVC %>% 
      left_join(llr_brand,by="brand") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_brand) 

   trn = llr_brand_long %>% filter(dsn == "train") %>% select(orderID,couponCol,llr_brand) 
   val = llr_brand_long %>% filter(dsn == "validation") %>% select(orderID,couponCol,llr_brand) 
   cls = llr_brand_long %>% filter(dsn == "class") %>% select(orderID,couponCol,llr_brand) 

   llr_brand_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brand_long,"../features/feature_files/llr_brand_long_set1.rds")

   #save the results to RDS in WIDE format
   llr_brand_wide = TVC %>% left_join(llr_brand,by="brand") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_brand) %>% 
      spread(couponCol,llr_brand) %>% 
      renm(c("orderID","dsn", "llr_brand1", "llr_brand2", "llr_brand3")) 

   trn = llr_brand_wide %>% filter(dsn == "train") %>% select(orderID,llr_brand1,llr_brand2,llr_brand3) 
   val = llr_brand_wide %>% filter(dsn == "validation") %>% select(orderID,llr_brand1,llr_brand2,llr_brand3) 
   cls = llr_brand_wide %>% filter(dsn == "class") %>% select(orderID,llr_brand1,llr_brand2,llr_brand3) 

   llr_brand_wide = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brand_wide,"../features/feature_files/llr_brand_wide_set1.rds")
```

*categoryIDs (aggregated)*
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE}
   # categoryIDs
   llr = compute_ll(as.character(H$categoryIDs),H$couponUsed,as.character(TVC$categoryIDs))
   llr_categoryIDs = data.frame("categoryIDs" = names(llr), "llr_categoryIDs" = llr) %>% arrange(categoryIDs) %>% unique

   #plot the results
   if(nrow(TVC) - sum(TVC$categoryIDs %in% llr_categoryIDs$categoryIDs)) warning("Things aren't adding up")
   qplot(as.numeric(gsub("cat","",categoryIDs)), llr_categoryIDs,data=llr_categoryIDs)

   #Isolate the features
   llr_categoryIDs_long = TVC %>% 
      left_join(llr_categoryIDs,by="categoryIDs") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_categoryIDs) 

   trn = llr_categoryIDs_long %>% filter(dsn == "train") %>% select(orderID,couponCol,llr_categoryIDs) 
   val = llr_categoryIDs_long %>% filter(dsn == "validation") %>% select(orderID,couponCol,llr_categoryIDs) 
   cls = llr_categoryIDs_long %>% filter(dsn == "class") %>% select(orderID,couponCol,llr_categoryIDs) 

   llr_categoryIDs_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_categoryIDs_long,"../features/feature_files/llr_categoryIDs_agg_long_set1.rds")

   #save the results to RDS in WIDE format
   llr_categoryIDs_wide = TVC %>% left_join(llr_categoryIDs,by="categoryIDs") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_categoryIDs) %>% 
      spread(couponCol,llr_categoryIDs) %>% 
      renm(c("orderID","dsn", "llr_categoryIDs1", "llr_categoryIDs2", "llr_categoryIDs3")) 

   trn = llr_categoryIDs_wide %>% filter(dsn == "train") %>% select(orderID,llr_categoryIDs1,llr_categoryIDs2,llr_categoryIDs3) 
   val = llr_categoryIDs_wide %>% filter(dsn == "validation") %>% select(orderID,llr_categoryIDs1,llr_categoryIDs2,llr_categoryIDs3) 
   cls = llr_categoryIDs_wide %>% filter(dsn == "class") %>% select(orderID,llr_categoryIDs1,llr_categoryIDs2,llr_categoryIDs3) 

   llr_categoryIDs_wide = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_categoryIDs_wide,"../features/feature_files/llr_categoryIDs_agg_wide_set1.rds")
```

*categoryIDs (individually)*

We may need to compute statistics with respect to each category apart from the aggregated one:
<!--- R code (No Results in Document) -->
```{r cache=TRUE}
   # categoryIDs individually
   source("./R/splitColumn.R")
   TVC.cat = splitColumn(TVC,"categoryIDs","orderID",splitby=":") %>% 
      select(orderID, couponCol, categoryIDs1, categoryIDs2, categoryIDs3, categoryIDs4, categoryIDs5) %>%
      gather(tmp, categoryID, -orderID, -couponCol) %>%
      mutate(categoryEntry = gsub("categoryIDs","",tmp)) %>%
      select(orderID, couponCol, categoryEntry, categoryID) %>%
      left_join(TVC,by=c("orderID","couponCol")) %>%
      arrange(orderID, couponCol, categoryEntry) %>%
      filter(!is.na(categoryID))

   H.cat = splitColumn(H,"categoryIDs","orderID",splitby=":") %>% 
      select(orderID, couponCol, categoryIDs1, categoryIDs2, categoryIDs3, categoryIDs4, categoryIDs5) %>%
      gather(tmp, categoryID, -orderID, -couponCol) %>%
      mutate(categoryEntry = gsub("categoryIDs","",tmp)) %>%
      select(orderID, couponCol, categoryEntry, categoryID) %>%
      left_join(H,by=c("orderID","couponCol")) %>%
      arrange(orderID, couponCol, categoryEntry) %>%
      filter(!is.na(categoryID))
```

<!--- R code (No Results in Document) -->
```{r cache=TRUE}
   # categoryID 
   llr = compute_ll(as.character(H.cat$categoryID),H.cat$couponUsed,as.character(TVC.cat$categoryID))
   llr_categoryID = data.frame("categoryID" = names(llr), "llr_categoryID" = llr) %>% arrange(categoryID) %>% unique %>% arrange(categoryID)

   #plot the results
   if(nrow(TVC.cat) - sum(TVC.cat$categoryID %in% llr_categoryID$categoryID)) warning("Things aren't adding up")
   qplot(gsub("cat","",categoryID), llr_categoryID,data=llr_categoryID,xlab="categoryID")

   #Isolate the features (long, long)
   llr_categoryID_long_long = TVC.cat %>% 
      left_join(llr_categoryID,by="categoryID") %>% 
      arrange(orderID,couponCol,categoryEntry) %>% 
      select(orderID,couponCol,categoryEntry,dsn,llr_categoryID) 

   trn = llr_categoryID_long_long %>% filter(dsn == "train") %>% select(orderID,couponCol,categoryEntry,llr_categoryID) 
   val = llr_categoryID_long_long %>% filter(dsn == "validation") %>% select(orderID,couponCol,categoryEntry,llr_categoryID) 
   cls = llr_categoryID_long_long %>% filter(dsn == "class") %>% select(orderID,couponCol,categoryEntry,llr_categoryID) 

   llr_categoryIDs_long_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_categoryIDs_long_long,"../features/feature_files/llr_categoryIDs_ind_long_long_set1.rds")

   #Isolate the features (long)
   llr_categoryID_long = TVC.cat %>% 
         left_join(llr_categoryID,by="categoryID") %>% 
         arrange(orderID,couponCol,categoryEntry) %>% 
         select(orderID,couponCol,categoryEntry,dsn,llr_categoryID) %>%
         spread(categoryEntry,llr_categoryID) %>%
         arrange(orderID,couponCol) %>% 
         renm(c("orderID","couponCol","dsn","llr_categoryIDs1", "llr_categoryIDs2", "llr_categoryIDs3", "llr_categoryIDs4", "llr_categoryIDs5")) 

   trn = llr_categoryID_long %>% filter(dsn == "train") %>% select(orderID,couponCol,llr_categoryIDs1,llr_categoryIDs2,llr_categoryIDs3,llr_categoryIDs4,llr_categoryIDs5)
   val = llr_categoryID_long %>% filter(dsn == "validation") %>% select(orderID,couponCol,llr_categoryIDs1,llr_categoryIDs2,llr_categoryIDs3,llr_categoryIDs4,llr_categoryIDs5)
   cls = llr_categoryID_long %>% filter(dsn == "class") %>% select(orderID,couponCol,llr_categoryIDs1,llr_categoryIDs2,llr_categoryIDs3,llr_categoryIDs4,llr_categoryIDs5)

   llr_categoryIDs_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_categoryIDs_long,"../features/feature_files/llr_categoryIDs_ind_long_set1.rds")

   #Isolate the features (wide)
   llr_categoryID_wide = TVC.cat %>% 
         left_join(llr_categoryID,by="categoryID") %>% 
         arrange(orderID,couponCol,categoryEntry) %>% 
         mutate(entryid = paste0("llr_cpnCol",couponCol,"_catEntry",categoryEntry)) %>%
         select(orderID,dsn,entryid,llr_categoryID) %>%
         spread(entryid,llr_categoryID) %>%
         arrange(orderID,dsn)

   trn = llr_categoryID_wide %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_categoryID_wide %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_categoryID_wide %>% filter(dsn == "class") %>% select(-dsn)

   llr_categoryIDs_wide = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_categoryIDs_wide,"../features/feature_files/llr_categoryIDs_ind_wide_set1.rds")

```

## Created Variables

*couponCol*
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE}
   # couponCol
   llr = compute_ll(as.character(H$couponCol),H$couponUsed,as.character(TVC$couponCol))
   llr_couponCol = data.frame("couponCol" = names(llr), "llr_couponCol" = llr) %>% arrange(couponCol) %>% unique
   llr_couponCol$couponCol = as.character(llr_couponCol$couponCol)

   #plot the results
   if(nrow(TVC) - sum(TVC$couponCol %in% llr_couponCol$couponCol)) warning("Things aren't adding up")
   qplot(as.numeric(gsub("cpn","",couponCol)), llr_couponCol,data=llr_couponCol)

   #Isolate the features
   llr_couponCol_long = 
   TVC %>% 
      left_join(llr_couponCol,by="couponCol") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_couponCol)

   trn = llr_couponCol_long %>% filter(dsn == "train") %>% select(orderID,couponCol,llr_couponCol) 
   val = llr_couponCol_long %>% filter(dsn == "validation") %>% select(orderID,couponCol,llr_couponCol) 
   cls = llr_couponCol_long %>% filter(dsn == "class") %>% select(orderID,couponCol,llr_couponCol) 

   llr_couponCol_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_couponCol_long,"../features/feature_files/llr_couponCol_long_set1.rds")

   #save the results to RDS in WIDE format
   llr_couponCol_wide = TVC %>% left_join(llr_couponCol,by="couponCol") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_couponCol) %>% 
      spread(couponCol,llr_couponCol) %>% 
      renm(c("orderID","dsn", "llr_couponCol1", "llr_couponCol2", "llr_couponCol3")) 

   trn = llr_couponCol_wide %>% filter(dsn == "train") %>% select(orderID,llr_couponCol1,llr_couponCol2,llr_couponCol3) 
   val = llr_couponCol_wide %>% filter(dsn == "validation") %>% select(orderID,llr_couponCol1,llr_couponCol2,llr_couponCol3) 
   cls = llr_couponCol_wide %>% filter(dsn == "class") %>% select(orderID,llr_couponCol1,llr_couponCol2,llr_couponCol3) 

   llr_couponCol_wide = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_couponCol_wide,"../features/feature_files/llr_couponCol_wide.rds")
```

*couponsReceivedDoW*
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE}
   # couponsReceivedDoW
   llr = compute_ll(as.character(H$couponsReceivedDoW),H$couponUsed,as.character(TVC$couponsReceivedDoW))
   llr_couponsReceivedDoW = data.frame("couponsReceivedDoW" = names(llr), "llr_couponsReceivedDoW" = llr) %>% arrange(couponsReceivedDoW) %>% unique

   #plot the results
   if(nrow(TVC) - sum(TVC$couponsReceivedDoW %in% llr_couponsReceivedDoW$couponsReceivedDoW)) warning("Things aren't adding up")
   qplot(couponsReceivedDoW, llr_couponsReceivedDoW,data=llr_couponsReceivedDoW)

   #Isolate the features
   llr_couponsReceivedDoW_long = TVC %>% 
      left_join(llr_couponsReceivedDoW,by="couponsReceivedDoW") %>% 
      arrange(orderID,couponsReceivedDoW) %>% 
      select(orderID,couponsReceivedDoW,dsn,llr_couponsReceivedDoW) 

   trn = llr_couponsReceivedDoW_long %>% filter(dsn == "train") %>% select(orderID,couponsReceivedDoW,llr_couponsReceivedDoW) 
   val = llr_couponsReceivedDoW_long %>% filter(dsn == "validation") %>% select(orderID,couponsReceivedDoW,llr_couponsReceivedDoW) 
   cls = llr_couponsReceivedDoW_long %>% filter(dsn == "class") %>% select(orderID,couponsReceivedDoW,llr_couponsReceivedDoW) 

   llr_couponsReceivedDoW_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_couponsReceivedDoW_long,"../features/feature_files/llr_couponsReceivedDoW_long_set1.rds")

   #save the results to RDS in WIDE format
   llr_couponsReceivedDoW_wide = 
   TVC %>% left_join(llr_couponsReceivedDoW,by="couponsReceivedDoW") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_couponsReceivedDoW) %>% 
      spread(couponCol,llr_couponsReceivedDoW) %>% 
      renm(c("orderID","dsn", "llr_couponsReceivedDoW1", "llr_couponsReceivedDoW2", "llr_couponsReceivedDoW3")) 

   trn = llr_couponsReceivedDoW_wide %>% filter(dsn == "train") %>% select(orderID,llr_couponsReceivedDoW1,llr_couponsReceivedDoW2,llr_couponsReceivedDoW3) 
   val = llr_couponsReceivedDoW_wide %>% filter(dsn == "validation") %>% select(orderID,llr_couponsReceivedDoW1,llr_couponsReceivedDoW2,llr_couponsReceivedDoW3) 
   cls = llr_couponsReceivedDoW_wide %>% filter(dsn == "class") %>% select(orderID,llr_couponsReceivedDoW1,llr_couponsReceivedDoW2,llr_couponsReceivedDoW3) 

   llr_couponsReceivedDoW_wide = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_couponsReceivedDoW_wide,"../features/feature_files/llr_couponsReceivedDoW_wide.rds")
```

*orderTimeDoW*
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=TRUE}
   # orderTimeDoW
   llr = compute_ll(as.character(H$orderTimeDoW),H$couponUsed,as.character(TVC$orderTimeDoW))
   llr_orderTimeDoW = data.frame("orderTimeDoW" = names(llr), "llr_orderTimeDoW" = llr) %>% arrange(orderTimeDoW) %>% unique

   #plot the results
   if(nrow(TVC) - sum(TVC$orderTimeDoW %in% llr_orderTimeDoW$orderTimeDoW)) warning("Things aren't adding up")
   qplot(orderTimeDoW, llr_orderTimeDoW,data=llr_orderTimeDoW)

   #Isolate the features
   llr_orderTimeDoW_long = TVC %>% 
      left_join(llr_orderTimeDoW,by="orderTimeDoW") %>% 
      arrange(orderID,orderTimeDoW) %>% 
      select(orderID,orderTimeDoW,dsn,llr_orderTimeDoW) 

   trn = llr_orderTimeDoW_long %>% filter(dsn == "train") %>% select(orderID,orderTimeDoW,llr_orderTimeDoW) 
   val = llr_orderTimeDoW_long %>% filter(dsn == "validation") %>% select(orderID,orderTimeDoW,llr_orderTimeDoW) 
   cls = llr_orderTimeDoW_long %>% filter(dsn == "class") %>% select(orderID,orderTimeDoW,llr_orderTimeDoW) 

   llr_orderTimeDoW_long = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_orderTimeDoW_long,"../features/feature_files/llr_orderTimeDoW_long_set1.rds")

   #save the results to RDS in WIDE format
   llr_orderTimeDoW_wide = TVC %>% left_join(llr_orderTimeDoW,by="orderTimeDoW") %>% 
      arrange(orderID,couponCol) %>% 
      select(orderID,couponCol,dsn,llr_orderTimeDoW) %>% 
      spread(couponCol,llr_orderTimeDoW) %>% 
      renm(c("orderID","dsn", "llr_orderTimeDoW1", "llr_orderTimeDoW2", "llr_orderTimeDoW3")) 

   trn = llr_orderTimeDoW_wide %>% filter(dsn == "train") %>% select(orderID,llr_orderTimeDoW1,llr_orderTimeDoW2,llr_orderTimeDoW3) 
   val = llr_orderTimeDoW_wide %>% filter(dsn == "validation") %>% select(orderID,llr_orderTimeDoW1,llr_orderTimeDoW2,llr_orderTimeDoW3) 
   cls = llr_orderTimeDoW_wide %>% filter(dsn == "class") %>% select(orderID,llr_orderTimeDoW1,llr_orderTimeDoW2,llr_orderTimeDoW3) 

   llr_orderTimeDoW_wide = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_orderTimeDoW_wide,"../features/feature_files/llr_orderTimeDoW_wide.rds")
```

      
# Calculating Coupon 2-Way Likelihoods

We have a sligthly more complicated task on this one:
<!--- two-way-choices: R code (No Results in Document) -->
```{r two-way-choices,cache=TRUE}
   names(TVC)[-c(1,2,4,5,6,7,11,12,16,17:22,24:25,31)]
```

## userID and 
*couponsReceivedDoW* (as `llr_userXrecDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedDoW 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$couponsReceivedDoW), H$couponUsed, as.character(TVC$userID), as.character(TVC$couponsReceivedDoW))
  llr_userXrecDoW = data.frame("userID" = TVC$userID, "couponsReceivedDoW" = TVC$couponsReceivedDoW, "llr_userXrecDoW" = llr) %>% arrange(userID) %>%
  
  ggplot(data=llr_userXrecDoW,aes(x=userID, y=couponsReceivedDoW, size = llr_userXrecDoW),alpha=.1) + geom_point()
  qplot(userID,llr_userXrecDoW,data=llr_userXrecDoW, geom='line', group=couponsReceivedDoW, facets = couponsReceivedDoW ~ .)

  TVC %>% left_join(llr_userXrecDoW, by=c("userID","couponsReceivedDoW")) %>%
     select(orderID,userID,dsn,couponsReceivedDoW,llr_userXrecDoW,couponUsed) %>%
     ggplot(aes(x=couponsReceivedDoW,y=llr_userXrecDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXrecDoW = TVC %>% 
     left_join(llr_userXrecDoW, by=c("userID","couponsReceivedDoW")) %>%
     select(orderID,dsn,llr_userXrecDoW)

   trn = llr_userXrecDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXrecDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXrecDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXrecDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXrecDoW,"../features/feature_files/llr_userXrecDoW.rds")
```

*couponsReceivedFriSat* (as `llr_userXrecFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedFriSat 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$couponsReceivedFriSat), H$couponUsed, as.character(TVC$userID), as.character(TVC$couponsReceivedFriSat))
  llr_userXrecFS = data.frame("userID" = TVC$userID, "couponsReceivedFriSat" = TVC$couponsReceivedFriSat, "llr_userXrecFS" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXrecFS,aes(x=userID, y=couponsReceivedFriSat, size = llr_userXrecFS),alpha=.1) + geom_point()
  qplot(userID,llr_userXrecFS,data=llr_userXrecFS, geom='line', group=couponsReceivedFriSat, facets = couponsReceivedFriSat ~ .)

  TVC %>% left_join(llr_userXrecFS, by=c("userID","couponsReceivedFriSat")) %>%
     select(orderID,userID,dsn,couponsReceivedFriSat,llr_userXrecFS,couponUsed) %>%
     ggplot(aes(x=couponsReceivedFriSat,y=llr_userXrecFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXrecFS = TVC %>% 
     left_join(llr_userXrecFS, by=c("userID","couponsReceivedFriSat")) %>%
     select(orderID,dsn,llr_userXrecFS)

   trn = llr_userXrecFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXrecFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXrecFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXrecFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXrecFS,"../features/feature_files/llr_userXrecFS.rds")
```

*couponsReceivedWeekend* (as `llr_userXrecWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedWeekend 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$couponsReceivedWeekend), H$couponUsed, as.character(TVC$userID), as.character(TVC$couponsReceivedWeekend))
  llr_userXrecWknd = data.frame("userID" = TVC$userID, "couponsReceivedWeekend" = TVC$couponsReceivedWeekend, "llr_userXrecWknd" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXrecWknd,aes(x=userID, y=couponsReceivedWeekend, size = llr_userXrecWknd),alpha=.1) + geom_point()
  qplot(userID,llr_userXrecWknd,data=llr_userXrecWknd, geom='line', group=couponsReceivedWeekend, facets = couponsReceivedWeekend ~ .)

  TVC %>% left_join(llr_userXrecWknd, by=c("userID","couponsReceivedWeekend")) %>%
     select(orderID,userID,dsn,couponsReceivedWeekend,llr_userXrecWknd,couponUsed) %>%
     ggplot(aes(x=couponsReceivedWeekend,y=llr_userXrecWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXrecWknd = TVC %>% 
     left_join(llr_userXrecWknd, by=c("userID","couponsReceivedWeekend")) %>%
     select(orderID,dsn,llr_userXrecWknd)

   trn = llr_userXrecWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXrecWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXrecWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXrecWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXrecWknd,"../features/feature_files/llr_userXrecWknd.rds")
```

*orderTimeDoW* (as `llr_userXordDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeDoW 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$orderTimeDoW), H$couponUsed, as.character(TVC$userID), as.character(TVC$orderTimeDoW))
  llr_userXordDoW = data.frame("userID" = TVC$userID, "orderTimeDoW" = TVC$orderTimeDoW, "llr_userXordDoW" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXordDoW,aes(x=userID, y=orderTimeDoW, size = llr_userXordDoW),alpha=.1) + geom_point()
  qplot(userID,llr_userXordDoW,data=llr_userXordDoW, geom='line', group=orderTimeDoW, facets = orderTimeDoW ~ .)

  TVC %>% left_join(llr_userXordDoW, by=c("userID","orderTimeDoW")) %>%
     select(orderID,userID,dsn,orderTimeDoW,llr_userXordDoW,couponUsed) %>%
     ggplot(aes(x=orderTimeDoW,y=llr_userXordDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXordDoW = TVC %>% 
     left_join(llr_userXordDoW, by=c("userID","orderTimeDoW")) %>%
     select(orderID,dsn,llr_userXordDoW)

   trn = llr_userXordDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXordDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXordDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXordDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXordDoW,"../features/feature_files/llr_userXordDoW.rds")
```

*orderTimeFriSat* (as `llr_userXordFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeFriSat 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$orderTimeFriSat), H$couponUsed, as.character(TVC$userID), as.character(TVC$orderTimeFriSat))
  llr_userXordFS = data.frame("userID" = TVC$userID, "orderTimeFriSat" = TVC$orderTimeFriSat, "llr_userXordFS" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXordFS,aes(x=userID, y=orderTimeFriSat, size = llr_userXordFS),alpha=.1) + geom_point()
  qplot(userID,llr_userXordFS,data=llr_userXordFS, geom='line', group=orderTimeFriSat, facets = orderTimeFriSat ~ .)

  TVC %>% left_join(llr_userXordFS, by=c("userID","orderTimeFriSat")) %>%
     select(orderID,userID,dsn,orderTimeFriSat,llr_userXordFS,couponUsed) %>%
     ggplot(aes(x=orderTimeFriSat,y=llr_userXordFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXordFS = TVC %>% 
     left_join(llr_userXordFS, by=c("userID","orderTimeFriSat")) %>%
     select(orderID,dsn,llr_userXordFS)

   trn = llr_userXordFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXordFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXordFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXordFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXordFS,"../features/feature_files/llr_userXordFS.rds")
```

*orderTimeWeekend* (as `llr_userXordWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeWeekend 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$orderTimeWeekend), H$couponUsed, as.character(TVC$userID), as.character(TVC$orderTimeWeekend))
  llr_userXordWknd = data.frame("userID" = TVC$userID, "orderTimeWeekend" = TVC$orderTimeWeekend, "llr_userXordWknd" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXordWknd,aes(x=userID, y=orderTimeWeekend, size = llr_userXordWknd),alpha=.1) + geom_point()
  qplot(userID,llr_userXordWknd,data=llr_userXordWknd, geom='line', group=orderTimeWeekend, facets = orderTimeWeekend ~ .)

  TVC %>% left_join(llr_userXordWknd, by=c("userID","orderTimeWeekend")) %>%
     select(orderID,userID,dsn,orderTimeWeekend,llr_userXordWknd,couponUsed) %>%
     ggplot(aes(x=orderTimeWeekend,y=llr_userXordWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXordWknd = TVC %>% 
     left_join(llr_userXordWknd, by=c("userID","orderTimeWeekend")) %>%
     select(orderID,dsn,llr_userXordWknd)

   trn = llr_userXordWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXordWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXordWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXordWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXordWknd,"../features/feature_files/llr_userXordWknd.rds")
```

*reward* (as `llr_userXrwrd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # reward 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$reward), H$couponUsed, as.character(TVC$userID), as.character(TVC$reward))
  llr_userXrwrd = data.frame("userID" = TVC$userID, "reward" = TVC$reward, "llr_userXrwrd" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXrwrd,aes(x=userID, y=reward, size = llr_userXrwrd),alpha=.1) + geom_point()
  qplot(userID,llr_userXrwrd,data=llr_userXrwrd, geom='line', group=reward, facets = reward ~ .)

  TVC %>% left_join(llr_userXrwrd, by=c("userID","reward")) %>%
     select(orderID,userID,dsn,reward,llr_userXrwrd,couponUsed) %>%
     ggplot(aes(x=reward,y=llr_userXrwrd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXrwrd = TVC %>% 
     left_join(llr_userXrwrd, by=c("userID","reward")) %>%
     select(orderID,dsn,llr_userXrwrd)

   trn = llr_userXrwrd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXrwrd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXrwrd %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXrwrd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXrwrd,"../features/feature_files/llr_userXrwrd.rds")
```

*premiumProduct* (as `llr_userXluxury`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # premiumProduct 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$premiumProduct), H$couponUsed, as.character(TVC$userID), as.character(TVC$premiumProduct))
  llr_userXluxury = data.frame("userID" = TVC$userID, "premiumProduct" = TVC$premiumProduct, "llr_userXluxury" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXluxury,aes(x=userID, y=premiumProduct, size = llr_userXluxury),alpha=.1) + geom_point()
  qplot(userID,llr_userXluxury,data=llr_userXluxury, geom='line', group=premiumProduct, facets = premiumProduct ~ .)

  TVC %>% left_join(llr_userXluxury, by=c("userID","premiumProduct")) %>%
     select(orderID,userID,dsn,premiumProduct,llr_userXluxury,couponUsed) %>%
     ggplot(aes(x=premiumProduct,y=llr_userXluxury,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXluxury = TVC %>% 
     left_join(llr_userXluxury, by=c("userID","premiumProduct")) %>%
     select(orderID,dsn,llr_userXluxury)

   trn = llr_userXluxury %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXluxury %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXluxury %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXluxury = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXluxury,"../features/feature_files/llr_userXluxury.rds")
```

*brand* (as `llr_userXbrnd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # brand 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$brand), H$couponUsed, as.character(TVC$userID), as.character(TVC$brand))
  llr_userXbrnd = data.frame("userID" = TVC$userID, "brand" = TVC$brand, "llr_userXbrnd" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXbrnd,aes(x=userID, y=brand, size = llr_userXbrnd),alpha=.1) + geom_point()
  qplot(userID,llr_userXbrnd,data=llr_userXbrnd, geom='line', group=brand, facets = brand ~ .)

  TVC %>% left_join(llr_userXbrnd, by=c("userID","brand")) %>%
     select(orderID,userID,dsn,brand,llr_userXbrnd,couponUsed) %>%
     ggplot(aes(x=brand,y=llr_userXbrnd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXbrnd = TVC %>% 
     left_join(llr_userXbrnd, by=c("userID","brand")) %>%
     select(orderID,dsn,llr_userXbrnd)

   trn = llr_userXbrnd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXbrnd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXbrnd %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXbrnd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXbrnd,"../features/feature_files/llr_userXbrnd.rds")
```

*productGroup* (as `llr_userXprod`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # productGroup 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$productGroup), H$couponUsed, as.character(TVC$userID), as.character(TVC$productGroup))
  llr_userXprod = data.frame("userID" = TVC$userID, "productGroup" = TVC$productGroup, "llr_userXprod" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXprod,aes(x=userID, y=productGroup, size = llr_userXprod),alpha=.1) + geom_point()
  qplot(userID,llr_userXprod,data=llr_userXprod, geom='line', group=productGroup, facets = productGroup ~ .)

  TVC %>% left_join(llr_userXprod, by=c("userID","productGroup")) %>%
     select(orderID,userID,dsn,productGroup,llr_userXprod,couponUsed) %>%
     ggplot(aes(x=productGroup,y=llr_userXprod,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXprod = TVC %>% 
     left_join(llr_userXprod, by=c("userID","productGroup")) %>%
     select(orderID,dsn,llr_userXprod)

   trn = llr_userXprod %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXprod %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXprod %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXprod = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXprod,"../features/feature_files/llr_userXprod.rds")
```

*couponCol* (as `llr_userXcpncol`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponCol 
  llr = compute_ll_2w(as.character(H$userID), as.character(H$couponCol), H$couponUsed, as.character(TVC$userID), as.character(TVC$couponCol))
  llr_userXcpncol = data.frame("userID" = TVC$userID, "couponCol" = TVC$couponCol, "llr_userXcpncol" = llr) %>% arrange(userID)
  
  ggplot(data=llr_userXcpncol,aes(x=userID, y=couponCol, size = llr_userXcpncol),alpha=.1) + geom_point()
  qplot(userID,llr_userXcpncol,data=llr_userXcpncol, geom='line', group=couponCol, facets = couponCol ~ .)

  TVC %>% left_join(llr_userXcpncol, by=c("userID","couponCol")) %>%
     select(orderID,userID,dsn,couponCol,llr_userXcpncol,couponUsed) %>%
     ggplot(aes(x=couponCol,y=llr_userXcpncol,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_userXcpncol = TVC %>% 
     left_join(llr_userXcpncol, by=c("userID","couponCol")) %>%
     select(orderID,dsn,llr_userXcpncol)

   trn = llr_userXcpncol %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_userXcpncol %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_userXcpncol %>% filter(dsn == "class") %>% select(-dsn)

   llr_userXcpncol = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_userXcpncol,"../features/feature_files/llr_userXcpncol.rds")
```

## reward and 
*couponsReceivedDoW* (as `llr_rewardXrecDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedDoW 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$couponsReceivedDoW), H$couponUsed, as.character(TVC$reward), as.character(TVC$couponsReceivedDoW))
  llr_rewardXrecDoW = data.frame("reward" = TVC$reward, "couponsReceivedDoW" = TVC$couponsReceivedDoW, "llr_rewardXrecDoW" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXrecDoW,aes(x=reward, y=couponsReceivedDoW, size = llr_rewardXrecDoW),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXrecDoW,data=llr_rewardXrecDoW, geom='line', group=couponsReceivedDoW, facets = couponsReceivedDoW ~ .)

  TVC %>% left_join(llr_rewardXrecDoW, by=c("reward","couponsReceivedDoW")) %>%
     select(orderID,reward,dsn,couponsReceivedDoW,llr_rewardXrecDoW,couponUsed) %>%
     ggplot(aes(x=couponsReceivedDoW,y=llr_rewardXrecDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXrecDoW = TVC %>% 
     left_join(llr_rewardXrecDoW, by=c("reward","couponsReceivedDoW")) %>%
     select(orderID,dsn,llr_rewardXrecDoW)

   trn = llr_rewardXrecDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXrecDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXrecDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXrecDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXrecDoW,"../features/feature_files/llr_rewardXrecDoW.rds")
```

*couponsReceivedFriSat* (as `llr_rewardXrecFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedFriSat 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$couponsReceivedFriSat), H$couponUsed, as.character(TVC$reward), as.character(TVC$couponsReceivedFriSat))
  llr_rewardXrecFS = data.frame("reward" = TVC$reward, "couponsReceivedFriSat" = TVC$couponsReceivedFriSat, "llr_rewardXrecFS" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXrecFS,aes(x=reward, y=couponsReceivedFriSat, size = llr_rewardXrecFS),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXrecFS,data=llr_rewardXrecFS, geom='line', group=couponsReceivedFriSat, facets = couponsReceivedFriSat ~ .)

  TVC %>% left_join(llr_rewardXrecFS, by=c("reward","couponsReceivedFriSat")) %>%
     select(orderID,reward,dsn,couponsReceivedFriSat,llr_rewardXrecFS,couponUsed) %>%
     ggplot(aes(x=couponsReceivedFriSat,y=llr_rewardXrecFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXrecFS = TVC %>% 
     left_join(llr_rewardXrecFS, by=c("reward","couponsReceivedFriSat")) %>%
     select(orderID,dsn,llr_rewardXrecFS)

   trn = llr_rewardXrecFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXrecFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXrecFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXrecFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXrecFS,"../features/feature_files/llr_rewardXrecFS.rds")
```

*couponsReceivedWeekend* (as `llr_rewardXrecWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedWeekend 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$couponsReceivedWeekend), H$couponUsed, as.character(TVC$reward), as.character(TVC$couponsReceivedWeekend))
  llr_rewardXrecWknd = data.frame("reward" = TVC$reward, "couponsReceivedWeekend" = TVC$couponsReceivedWeekend, "llr_rewardXrecWknd" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXrecWknd,aes(x=reward, y=couponsReceivedWeekend, size = llr_rewardXrecWknd),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXrecWknd,data=llr_rewardXrecWknd, geom='line', group=couponsReceivedWeekend, facets = couponsReceivedWeekend ~ .)

  TVC %>% left_join(llr_rewardXrecWknd, by=c("reward","couponsReceivedWeekend")) %>%
     select(orderID,reward,dsn,couponsReceivedWeekend,llr_rewardXrecWknd,couponUsed) %>%
     ggplot(aes(x=couponsReceivedWeekend,y=llr_rewardXrecWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXrecWknd = TVC %>% 
     left_join(llr_rewardXrecWknd, by=c("reward","couponsReceivedWeekend")) %>%
     select(orderID,dsn,llr_rewardXrecWknd)

   trn = llr_rewardXrecWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXrecWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXrecWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXrecWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXrecWknd,"../features/feature_files/llr_rewardXrecWknd.rds")
```

*orderTimeDoW* (as `llr_rewardXordDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeDoW 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$orderTimeDoW), H$couponUsed, as.character(TVC$reward), as.character(TVC$orderTimeDoW))
  llr_rewardXordDoW = data.frame("reward" = TVC$reward, "orderTimeDoW" = TVC$orderTimeDoW, "llr_rewardXordDoW" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXordDoW,aes(x=reward, y=orderTimeDoW, size = llr_rewardXordDoW),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXordDoW,data=llr_rewardXordDoW, geom='line', group=orderTimeDoW, facets = orderTimeDoW ~ .)

  TVC %>% left_join(llr_rewardXordDoW, by=c("reward","orderTimeDoW")) %>%
     select(orderID,reward,dsn,orderTimeDoW,llr_rewardXordDoW,couponUsed) %>%
     ggplot(aes(x=orderTimeDoW,y=llr_rewardXordDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXordDoW = TVC %>% 
     left_join(llr_rewardXordDoW, by=c("reward","orderTimeDoW")) %>%
     select(orderID,dsn,llr_rewardXordDoW)

   trn = llr_rewardXordDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXordDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXordDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXordDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXordDoW,"../features/feature_files/llr_rewardXordDoW.rds")
```

*orderTimeFriSat* (as `llr_rewardXordFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeFriSat 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$orderTimeFriSat), H$couponUsed, as.character(TVC$reward), as.character(TVC$orderTimeFriSat))
  llr_rewardXordFS = data.frame("reward" = TVC$reward, "orderTimeFriSat" = TVC$orderTimeFriSat, "llr_rewardXordFS" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXordFS,aes(x=reward, y=orderTimeFriSat, size = llr_rewardXordFS),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXordFS,data=llr_rewardXordFS, geom='line', group=orderTimeFriSat, facets = orderTimeFriSat ~ .)

  TVC %>% left_join(llr_rewardXordFS, by=c("reward","orderTimeFriSat")) %>%
     select(orderID,reward,dsn,orderTimeFriSat,llr_rewardXordFS,couponUsed) %>%
     ggplot(aes(x=orderTimeFriSat,y=llr_rewardXordFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXordFS = TVC %>% 
     left_join(llr_rewardXordFS, by=c("reward","orderTimeFriSat")) %>%
     select(orderID,dsn,llr_rewardXordFS)

   trn = llr_rewardXordFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXordFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXordFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXordFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXordFS,"../features/feature_files/llr_rewardXordFS.rds")
```

*orderTimeWeekend* (as `llr_rewardXordWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeWeekend 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$orderTimeWeekend), H$couponUsed, as.character(TVC$reward), as.character(TVC$orderTimeWeekend))
  llr_rewardXordWknd = data.frame("reward" = TVC$reward, "orderTimeWeekend" = TVC$orderTimeWeekend, "llr_rewardXordWknd" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXordWknd,aes(x=reward, y=orderTimeWeekend, size = llr_rewardXordWknd),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXordWknd,data=llr_rewardXordWknd, geom='line', group=orderTimeWeekend, facets = orderTimeWeekend ~ .)

  TVC %>% left_join(llr_rewardXordWknd, by=c("reward","orderTimeWeekend")) %>%
     select(orderID,reward,dsn,orderTimeWeekend,llr_rewardXordWknd,couponUsed) %>%
     ggplot(aes(x=orderTimeWeekend,y=llr_rewardXordWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXordWknd = TVC %>% 
     left_join(llr_rewardXordWknd, by=c("reward","orderTimeWeekend")) %>%
     select(orderID,dsn,llr_rewardXordWknd)

   trn = llr_rewardXordWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXordWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXordWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXordWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXordWknd,"../features/feature_files/llr_rewardXordWknd.rds")
```

*premiumProduct* (as `llr_rewardXluxury`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # premiumProduct 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$premiumProduct), H$couponUsed, as.character(TVC$reward), as.character(TVC$premiumProduct))
  llr_rewardXluxury = data.frame("reward" = TVC$reward, "premiumProduct" = TVC$premiumProduct, "llr_rewardXluxury" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXluxury,aes(x=reward, y=premiumProduct, size = llr_rewardXluxury),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXluxury,data=llr_rewardXluxury, geom='line', group=premiumProduct, facets = premiumProduct ~ .)

  TVC %>% left_join(llr_rewardXluxury, by=c("reward","premiumProduct")) %>%
     select(orderID,reward,dsn,premiumProduct,llr_rewardXluxury,couponUsed) %>%
     ggplot(aes(x=premiumProduct,y=llr_rewardXluxury,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXluxury = TVC %>% 
     left_join(llr_rewardXluxury, by=c("reward","premiumProduct")) %>%
     select(orderID,dsn,llr_rewardXluxury)

   trn = llr_rewardXluxury %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXluxury %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXluxury %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXluxury = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXluxury,"../features/feature_files/llr_rewardXluxury.rds")
```

*brand* (as `llr_rewardXbrnd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # brand 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$brand), H$couponUsed, as.character(TVC$reward), as.character(TVC$brand))
  llr_rewardXbrnd = data.frame("reward" = TVC$reward, "brand" = TVC$brand, "llr_rewardXbrnd" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXbrnd,aes(x=reward, y=brand, size = llr_rewardXbrnd),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXbrnd,data=llr_rewardXbrnd, geom='line', group=brand, facets = brand ~ .)

  TVC %>% left_join(llr_rewardXbrnd, by=c("reward","brand")) %>%
     select(orderID,reward,dsn,brand,llr_rewardXbrnd,couponUsed) %>%
     ggplot(aes(x=brand,y=llr_rewardXbrnd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXbrnd = TVC %>% 
     left_join(llr_rewardXbrnd, by=c("reward","brand")) %>%
     select(orderID,dsn,llr_rewardXbrnd)

   trn = llr_rewardXbrnd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXbrnd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXbrnd %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXbrnd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXbrnd,"../features/feature_files/llr_rewardXbrnd.rds")
```

*productGroup* (as `llr_rewardXprod`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # productGroup 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$productGroup), H$couponUsed, as.character(TVC$reward), as.character(TVC$productGroup))
  llr_rewardXprod = data.frame("reward" = TVC$reward, "productGroup" = TVC$productGroup, "llr_rewardXprod" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXprod,aes(x=reward, y=productGroup, size = llr_rewardXprod),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXprod,data=llr_rewardXprod, geom='line', group=productGroup, facets = productGroup ~ .)

  TVC %>% left_join(llr_rewardXprod, by=c("reward","productGroup")) %>%
     select(orderID,reward,dsn,productGroup,llr_rewardXprod,couponUsed) %>%
     ggplot(aes(x=productGroup,y=llr_rewardXprod,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXprod = TVC %>% 
     left_join(llr_rewardXprod, by=c("reward","productGroup")) %>%
     select(orderID,dsn,llr_rewardXprod)

   trn = llr_rewardXprod %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXprod %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXprod %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXprod = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXprod,"../features/feature_files/llr_rewardXprod.rds")
```

*couponCol* (as `llr_rewardXcpncol`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponCol 
  llr = compute_ll_2w(as.character(H$reward), as.character(H$couponCol), H$couponUsed, as.character(TVC$reward), as.character(TVC$couponCol))
  llr_rewardXcpncol = data.frame("reward" = TVC$reward, "couponCol" = TVC$couponCol, "llr_rewardXcpncol" = llr) %>% arrange(reward)
  
  ggplot(data=llr_rewardXcpncol,aes(x=reward, y=couponCol, size = llr_rewardXcpncol),alpha=.1) + geom_point()
  qplot(reward,llr_rewardXcpncol,data=llr_rewardXcpncol, geom='line', group=couponCol, facets = couponCol ~ .)

  TVC %>% left_join(llr_rewardXcpncol, by=c("reward","couponCol")) %>%
     select(orderID,reward,dsn,couponCol,llr_rewardXcpncol,couponUsed) %>%
     ggplot(aes(x=couponCol,y=llr_rewardXcpncol,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_rewardXcpncol = TVC %>% 
     left_join(llr_rewardXcpncol, by=c("reward","couponCol")) %>%
     select(orderID,dsn,llr_rewardXcpncol)

   trn = llr_rewardXcpncol %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_rewardXcpncol %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_rewardXcpncol %>% filter(dsn == "class") %>% select(-dsn)

   llr_rewardXcpncol = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_rewardXcpncol,"../features/feature_files/llr_rewardXcpncol.rds")
```

## premiumProduct and 
*couponsReceivedDoW* (as `llr_luxuryXrecDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedDoW 
  llr = compute_ll_2w(as.character(H$premiumProduct), as.character(H$couponsReceivedDoW), H$couponUsed, as.character(TVC$premiumProduct), as.character(TVC$couponsReceivedDoW))
  llr_luxuryXrecDoW = data.frame("premiumProduct" = TVC$premiumProduct, "couponsReceivedDoW" = TVC$couponsReceivedDoW, "llr_luxuryXrecDoW" = llr) %>% arrange(premiumProduct)
  
  ggplot(data=llr_luxuryXrecDoW,aes(x=premiumProduct, y=couponsReceivedDoW, size = llr_luxuryXrecDoW),alpha=.1) + geom_point()
  qplot(premiumProduct,llr_luxuryXrecDoW,data=llr_luxuryXrecDoW, geom='line', group=couponsReceivedDoW, facets = couponsReceivedDoW ~ .)

  TVC %>% left_join(llr_luxuryXrecDoW, by=c("premiumProduct","couponsReceivedDoW")) %>%
     select(orderID,premiumProduct,dsn,couponsReceivedDoW,llr_luxuryXrecDoW,couponUsed) %>%
     ggplot(aes(x=couponsReceivedDoW,y=llr_luxuryXrecDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_luxuryXrecDoW = TVC %>% 
     left_join(llr_luxuryXrecDoW, by=c("premiumProduct","couponsReceivedDoW")) %>%
     select(orderID,dsn,llr_luxuryXrecDoW)

   trn = llr_luxuryXrecDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_luxuryXrecDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_luxuryXrecDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_luxuryXrecDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_luxuryXrecDoW,"../features/feature_files/llr_luxuryXrecDoW.rds")
```

*couponsReceivedFriSat* (as `llr_luxuryXrecFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedFriSat 
  llr = compute_ll_2w(as.character(H$premiumProduct), as.character(H$couponsReceivedFriSat), H$couponUsed, as.character(TVC$premiumProduct), as.character(TVC$couponsReceivedFriSat))
  llr_luxuryXrecFS = data.frame("premiumProduct" = TVC$premiumProduct, "couponsReceivedFriSat" = TVC$couponsReceivedFriSat, "llr_luxuryXrecFS" = llr) %>% arrange(premiumProduct)
  
  ggplot(data=llr_luxuryXrecFS,aes(x=premiumProduct, y=couponsReceivedFriSat, size = llr_luxuryXrecFS),alpha=.1) + geom_point()
  qplot(premiumProduct,llr_luxuryXrecFS,data=llr_luxuryXrecFS, geom='line', group=couponsReceivedFriSat, facets = couponsReceivedFriSat ~ .)

  TVC %>% left_join(llr_luxuryXrecFS, by=c("premiumProduct","couponsReceivedFriSat")) %>%
     select(orderID,premiumProduct,dsn,couponsReceivedFriSat,llr_luxuryXrecFS,couponUsed) %>%
     ggplot(aes(x=couponsReceivedFriSat,y=llr_luxuryXrecFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_luxuryXrecFS = TVC %>% 
     left_join(llr_luxuryXrecFS, by=c("premiumProduct","couponsReceivedFriSat")) %>%
     select(orderID,dsn,llr_luxuryXrecFS)

   trn = llr_luxuryXrecFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_luxuryXrecFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_luxuryXrecFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_luxuryXrecFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_luxuryXrecFS,"../features/feature_files/llr_luxuryXrecFS.rds")
```

*couponsReceivedWeekend* (as `llr_luxuryXrecWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedWeekend 
  llr = compute_ll_2w(as.character(H$premiumProduct), as.character(H$couponsReceivedWeekend), H$couponUsed, as.character(TVC$premiumProduct), as.character(TVC$couponsReceivedWeekend))
  llr_luxuryXrecWknd = data.frame("premiumProduct" = TVC$premiumProduct, "couponsReceivedWeekend" = TVC$couponsReceivedWeekend, "llr_luxuryXrecWknd" = llr) %>% arrange(premiumProduct)
  
  ggplot(data=llr_luxuryXrecWknd,aes(x=premiumProduct, y=couponsReceivedWeekend, size = llr_luxuryXrecWknd),alpha=.1) + geom_point()
  qplot(premiumProduct,llr_luxuryXrecWknd,data=llr_luxuryXrecWknd, geom='line', group=couponsReceivedWeekend, facets = couponsReceivedWeekend ~ .)

  TVC %>% left_join(llr_luxuryXrecWknd, by=c("premiumProduct","couponsReceivedWeekend")) %>%
     select(orderID,premiumProduct,dsn,couponsReceivedWeekend,llr_luxuryXrecWknd,couponUsed) %>%
     ggplot(aes(x=couponsReceivedWeekend,y=llr_luxuryXrecWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_luxuryXrecWknd = TVC %>% 
     left_join(llr_luxuryXrecWknd, by=c("premiumProduct","couponsReceivedWeekend")) %>%
     select(orderID,dsn,llr_luxuryXrecWknd)

   trn = llr_luxuryXrecWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_luxuryXrecWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_luxuryXrecWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_luxuryXrecWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_luxuryXrecWknd,"../features/feature_files/llr_luxuryXrecWknd.rds")
```

*orderTimeDoW* (as `llr_luxuryXordDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeDoW 
  llr = compute_ll_2w(as.character(H$premiumProduct), as.character(H$orderTimeDoW), H$couponUsed, as.character(TVC$premiumProduct), as.character(TVC$orderTimeDoW))
  llr_luxuryXordDoW = data.frame("premiumProduct" = TVC$premiumProduct, "orderTimeDoW" = TVC$orderTimeDoW, "llr_luxuryXordDoW" = llr) %>% arrange(premiumProduct)
  
  ggplot(data=llr_luxuryXordDoW,aes(x=premiumProduct, y=orderTimeDoW, size = llr_luxuryXordDoW),alpha=.1) + geom_point()
  qplot(premiumProduct,llr_luxuryXordDoW,data=llr_luxuryXordDoW, geom='line', group=orderTimeDoW, facets = orderTimeDoW ~ .)

  TVC %>% left_join(llr_luxuryXordDoW, by=c("premiumProduct","orderTimeDoW")) %>%
     select(orderID,premiumProduct,dsn,orderTimeDoW,llr_luxuryXordDoW,couponUsed) %>%
     ggplot(aes(x=orderTimeDoW,y=llr_luxuryXordDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_luxuryXordDoW = TVC %>% 
     left_join(llr_luxuryXordDoW, by=c("premiumProduct","orderTimeDoW")) %>%
     select(orderID,dsn,llr_luxuryXordDoW)

   trn = llr_luxuryXordDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_luxuryXordDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_luxuryXordDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_luxuryXordDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_luxuryXordDoW,"../features/feature_files/llr_luxuryXordDoW.rds")
```

*orderTimeFriSat* (as `llr_luxuryXordFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeFriSat 
  llr = compute_ll_2w(as.character(H$premiumProduct), as.character(H$orderTimeFriSat), H$couponUsed, as.character(TVC$premiumProduct), as.character(TVC$orderTimeFriSat))
  llr_luxuryXordFS = data.frame("premiumProduct" = TVC$premiumProduct, "orderTimeFriSat" = TVC$orderTimeFriSat, "llr_luxuryXordFS" = llr) %>% arrange(premiumProduct)
  
  ggplot(data=llr_luxuryXordFS,aes(x=premiumProduct, y=orderTimeFriSat, size = llr_luxuryXordFS),alpha=.1) + geom_point()
  qplot(premiumProduct,llr_luxuryXordFS,data=llr_luxuryXordFS, geom='line', group=orderTimeFriSat, facets = orderTimeFriSat ~ .)

  TVC %>% left_join(llr_luxuryXordFS, by=c("premiumProduct","orderTimeFriSat")) %>%
     select(orderID,premiumProduct,dsn,orderTimeFriSat,llr_luxuryXordFS,couponUsed) %>%
     ggplot(aes(x=orderTimeFriSat,y=llr_luxuryXordFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_luxuryXordFS = TVC %>% 
     left_join(llr_luxuryXordFS, by=c("premiumProduct","orderTimeFriSat")) %>%
     select(orderID,dsn,llr_luxuryXordFS)

   trn = llr_luxuryXordFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_luxuryXordFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_luxuryXordFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_luxuryXordFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_luxuryXordFS,"../features/feature_files/llr_luxuryXordFS.rds")
```

*orderTimeWeekend* (as `llr_luxuryXordWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeWeekend 
  llr = compute_ll_2w(as.character(H$premiumProduct), as.character(H$orderTimeWeekend), H$couponUsed, as.character(TVC$premiumProduct), as.character(TVC$orderTimeWeekend))
  llr_luxuryXordWknd = data.frame("premiumProduct" = TVC$premiumProduct, "orderTimeWeekend" = TVC$orderTimeWeekend, "llr_luxuryXordWknd" = llr) %>% arrange(premiumProduct)
  
  ggplot(data=llr_luxuryXordWknd,aes(x=premiumProduct, y=orderTimeWeekend, size = llr_luxuryXordWknd),alpha=.1) + geom_point()
  qplot(premiumProduct,llr_luxuryXordWknd,data=llr_luxuryXordWknd, geom='line', group=orderTimeWeekend, facets = orderTimeWeekend ~ .)

  TVC %>% left_join(llr_luxuryXordWknd, by=c("premiumProduct","orderTimeWeekend")) %>%
     select(orderID,premiumProduct,dsn,orderTimeWeekend,llr_luxuryXordWknd,couponUsed) %>%
     ggplot(aes(x=orderTimeWeekend,y=llr_luxuryXordWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_luxuryXordWknd = TVC %>% 
     left_join(llr_luxuryXordWknd, by=c("premiumProduct","orderTimeWeekend")) %>%
     select(orderID,dsn,llr_luxuryXordWknd)

   trn = llr_luxuryXordWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_luxuryXordWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_luxuryXordWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_luxuryXordWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_luxuryXordWknd,"../features/feature_files/llr_luxuryXordWknd.rds")
```

*brand* (as `llr_luxuryXbrnd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # brand 
  llr = compute_ll_2w(as.character(H$premiumProduct), as.character(H$brand), H$couponUsed, as.character(TVC$premiumProduct), as.character(TVC$brand))
  llr_luxuryXbrnd = data.frame("premiumProduct" = TVC$premiumProduct, "brand" = TVC$brand, "llr_luxuryXbrnd" = llr) %>% arrange(premiumProduct)
  
  ggplot(data=llr_luxuryXbrnd,aes(x=premiumProduct, y=brand, size = llr_luxuryXbrnd),alpha=.1) + geom_point()
  qplot(premiumProduct,llr_luxuryXbrnd,data=llr_luxuryXbrnd, geom='line', group=brand, facets = brand ~ .)

  TVC %>% left_join(llr_luxuryXbrnd, by=c("premiumProduct","brand")) %>%
     select(orderID,premiumProduct,dsn,brand,llr_luxuryXbrnd,couponUsed) %>%
     ggplot(aes(x=brand,y=llr_luxuryXbrnd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_luxuryXbrnd = TVC %>% 
     left_join(llr_luxuryXbrnd, by=c("premiumProduct","brand")) %>%
     select(orderID,dsn,llr_luxuryXbrnd)

   trn = llr_luxuryXbrnd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_luxuryXbrnd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_luxuryXbrnd %>% filter(dsn == "class") %>% select(-dsn)

   llr_luxuryXbrnd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_luxuryXbrnd,"../features/feature_files/llr_luxuryXbrnd.rds")
```

*productGroup* (as `llr_luxuryXprod`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # productGroup 
  llr = compute_ll_2w(as.character(H$premiumProduct), as.character(H$productGroup), H$couponUsed, as.character(TVC$premiumProduct), as.character(TVC$productGroup))
  llr_luxuryXprod = data.frame("premiumProduct" = TVC$premiumProduct, "productGroup" = TVC$productGroup, "llr_luxuryXprod" = llr) %>% arrange(premiumProduct)
  
  ggplot(data=llr_luxuryXprod,aes(x=premiumProduct, y=productGroup, size = llr_luxuryXprod),alpha=.1) + geom_point()
  qplot(premiumProduct,llr_luxuryXprod,data=llr_luxuryXprod, geom='line', group=productGroup, facets = productGroup ~ .)

  TVC %>% left_join(llr_luxuryXprod, by=c("premiumProduct","productGroup")) %>%
     select(orderID,premiumProduct,dsn,productGroup,llr_luxuryXprod,couponUsed) %>%
     ggplot(aes(x=productGroup,y=llr_luxuryXprod,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_luxuryXprod = TVC %>% 
     left_join(llr_luxuryXprod, by=c("premiumProduct","productGroup")) %>%
     select(orderID,dsn,llr_luxuryXprod)

   trn = llr_luxuryXprod %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_luxuryXprod %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_luxuryXprod %>% filter(dsn == "class") %>% select(-dsn)

   llr_luxuryXprod = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_luxuryXprod,"../features/feature_files/llr_luxuryXprod.rds")
```

*couponCol* (as `llr_luxuryXcpncol`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponCol 
  llr = compute_ll_2w(as.character(H$premiumProduct), as.character(H$couponCol), H$couponUsed, as.character(TVC$premiumProduct), as.character(TVC$couponCol))
  llr_luxuryXcpncol = data.frame("premiumProduct" = TVC$premiumProduct, "couponCol" = TVC$couponCol, "llr_luxuryXcpncol" = llr) %>% arrange(premiumProduct)
  
  ggplot(data=llr_luxuryXcpncol,aes(x=premiumProduct, y=couponCol, size = llr_luxuryXcpncol),alpha=.1) + geom_point()
  qplot(premiumProduct,llr_luxuryXcpncol,data=llr_luxuryXcpncol, geom='line', group=couponCol, facets = couponCol ~ .)

  TVC %>% left_join(llr_luxuryXcpncol, by=c("premiumProduct","couponCol")) %>%
     select(orderID,premiumProduct,dsn,couponCol,llr_luxuryXcpncol,couponUsed) %>%
     ggplot(aes(x=couponCol,y=llr_luxuryXcpncol,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_luxuryXcpncol = TVC %>% 
     left_join(llr_luxuryXcpncol, by=c("premiumProduct","couponCol")) %>%
     select(orderID,dsn,llr_luxuryXcpncol)

   trn = llr_luxuryXcpncol %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_luxuryXcpncol %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_luxuryXcpncol %>% filter(dsn == "class") %>% select(-dsn)

   llr_luxuryXcpncol = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_luxuryXcpncol,"../features/feature_files/llr_luxuryXcpncol.rds")
```

## brand and 
*couponsReceivedDoW* (as `llr_brandXrecDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedDoW 
  llr = compute_ll_2w(as.character(H$brand), as.character(H$couponsReceivedDoW), H$couponUsed, as.character(TVC$brand), as.character(TVC$couponsReceivedDoW))
  llr_brandXrecDoW = data.frame("brand" = TVC$brand, "couponsReceivedDoW" = TVC$couponsReceivedDoW, "llr_brandXrecDoW" = llr) %>% arrange(brand)
  
  ggplot(data=llr_brandXrecDoW,aes(x=brand, y=couponsReceivedDoW, size = llr_brandXrecDoW),alpha=.1) + geom_point()
  qplot(brand,llr_brandXrecDoW,data=llr_brandXrecDoW, geom='line', group=couponsReceivedDoW, facets = couponsReceivedDoW ~ .)

  TVC %>% left_join(llr_brandXrecDoW, by=c("brand","couponsReceivedDoW")) %>%
     select(orderID,brand,dsn,couponsReceivedDoW,llr_brandXrecDoW,couponUsed) %>%
     ggplot(aes(x=couponsReceivedDoW,y=llr_brandXrecDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_brandXrecDoW = TVC %>% 
     left_join(llr_brandXrecDoW, by=c("brand","couponsReceivedDoW")) %>%
     select(orderID,dsn,llr_brandXrecDoW)

   trn = llr_brandXrecDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_brandXrecDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_brandXrecDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_brandXrecDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brandXrecDoW,"../features/feature_files/llr_brandXrecDoW.rds")
```

*couponsReceivedFriSat* (as `llr_brandXrecFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedFriSat 
  llr = compute_ll_2w(as.character(H$brand), as.character(H$couponsReceivedFriSat), H$couponUsed, as.character(TVC$brand), as.character(TVC$couponsReceivedFriSat))
  llr_brandXrecFS = data.frame("brand" = TVC$brand, "couponsReceivedFriSat" = TVC$couponsReceivedFriSat, "llr_brandXrecFS" = llr) %>% arrange(brand)
  
  ggplot(data=llr_brandXrecFS,aes(x=brand, y=couponsReceivedFriSat, size = llr_brandXrecFS),alpha=.1) + geom_point()
  qplot(brand,llr_brandXrecFS,data=llr_brandXrecFS, geom='line', group=couponsReceivedFriSat, facets = couponsReceivedFriSat ~ .)

  TVC %>% left_join(llr_brandXrecFS, by=c("brand","couponsReceivedFriSat")) %>%
     select(orderID,brand,dsn,couponsReceivedFriSat,llr_brandXrecFS,couponUsed) %>%
     ggplot(aes(x=couponsReceivedFriSat,y=llr_brandXrecFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_brandXrecFS = TVC %>% 
     left_join(llr_brandXrecFS, by=c("brand","couponsReceivedFriSat")) %>%
     select(orderID,dsn,llr_brandXrecFS)

   trn = llr_brandXrecFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_brandXrecFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_brandXrecFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_brandXrecFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brandXrecFS,"../features/feature_files/llr_brandXrecFS.rds")
```

*couponsReceivedWeekend* (as `llr_brandXrecWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedWeekend 
  llr = compute_ll_2w(as.character(H$brand), as.character(H$couponsReceivedWeekend), H$couponUsed, as.character(TVC$brand), as.character(TVC$couponsReceivedWeekend))
  llr_brandXrecWknd = data.frame("brand" = TVC$brand, "couponsReceivedWeekend" = TVC$couponsReceivedWeekend, "llr_brandXrecWknd" = llr) %>% arrange(brand)
  
  ggplot(data=llr_brandXrecWknd,aes(x=brand, y=couponsReceivedWeekend, size = llr_brandXrecWknd),alpha=.1) + geom_point()
  qplot(brand,llr_brandXrecWknd,data=llr_brandXrecWknd, geom='line', group=couponsReceivedWeekend, facets = couponsReceivedWeekend ~ .)

  TVC %>% left_join(llr_brandXrecWknd, by=c("brand","couponsReceivedWeekend")) %>%
     select(orderID,brand,dsn,couponsReceivedWeekend,llr_brandXrecWknd,couponUsed) %>%
     ggplot(aes(x=couponsReceivedWeekend,y=llr_brandXrecWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_brandXrecWknd = TVC %>% 
     left_join(llr_brandXrecWknd, by=c("brand","couponsReceivedWeekend")) %>%
     select(orderID,dsn,llr_brandXrecWknd)

   trn = llr_brandXrecWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_brandXrecWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_brandXrecWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_brandXrecWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brandXrecWknd,"../features/feature_files/llr_brandXrecWknd.rds")
```

*orderTimeDoW* (as `llr_brandXordDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeDoW 
  llr = compute_ll_2w(as.character(H$brand), as.character(H$orderTimeDoW), H$couponUsed, as.character(TVC$brand), as.character(TVC$orderTimeDoW))
  llr_brandXordDoW = data.frame("brand" = TVC$brand, "orderTimeDoW" = TVC$orderTimeDoW, "llr_brandXordDoW" = llr) %>% arrange(brand)
  
  ggplot(data=llr_brandXordDoW,aes(x=brand, y=orderTimeDoW, size = llr_brandXordDoW),alpha=.1) + geom_point()
  qplot(brand,llr_brandXordDoW,data=llr_brandXordDoW, geom='line', group=orderTimeDoW, facets = orderTimeDoW ~ .)

  TVC %>% left_join(llr_brandXordDoW, by=c("brand","orderTimeDoW")) %>%
     select(orderID,brand,dsn,orderTimeDoW,llr_brandXordDoW,couponUsed) %>%
     ggplot(aes(x=orderTimeDoW,y=llr_brandXordDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_brandXordDoW = TVC %>% 
     left_join(llr_brandXordDoW, by=c("brand","orderTimeDoW")) %>%
     select(orderID,dsn,llr_brandXordDoW)

   trn = llr_brandXordDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_brandXordDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_brandXordDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_brandXordDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brandXordDoW,"../features/feature_files/llr_brandXordDoW.rds")
```

*orderTimeFriSat* (as `llr_brandXordFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeFriSat 
  llr = compute_ll_2w(as.character(H$brand), as.character(H$orderTimeFriSat), H$couponUsed, as.character(TVC$brand), as.character(TVC$orderTimeFriSat))
  llr_brandXordFS = data.frame("brand" = TVC$brand, "orderTimeFriSat" = TVC$orderTimeFriSat, "llr_brandXordFS" = llr) %>% arrange(brand)
  
  ggplot(data=llr_brandXordFS,aes(x=brand, y=orderTimeFriSat, size = llr_brandXordFS),alpha=.1) + geom_point()
  qplot(brand,llr_brandXordFS,data=llr_brandXordFS, geom='line', group=orderTimeFriSat, facets = orderTimeFriSat ~ .)

  TVC %>% left_join(llr_brandXordFS, by=c("brand","orderTimeFriSat")) %>%
     select(orderID,brand,dsn,orderTimeFriSat,llr_brandXordFS,couponUsed) %>%
     ggplot(aes(x=orderTimeFriSat,y=llr_brandXordFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_brandXordFS = TVC %>% 
     left_join(llr_brandXordFS, by=c("brand","orderTimeFriSat")) %>%
     select(orderID,dsn,llr_brandXordFS)

   trn = llr_brandXordFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_brandXordFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_brandXordFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_brandXordFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brandXordFS,"../features/feature_files/llr_brandXordFS.rds")
```

*orderTimeWeekend* (as `llr_brandXordWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeWeekend 
  llr = compute_ll_2w(as.character(H$brand), as.character(H$orderTimeWeekend), H$couponUsed, as.character(TVC$brand), as.character(TVC$orderTimeWeekend))
  llr_brandXordWknd = data.frame("brand" = TVC$brand, "orderTimeWeekend" = TVC$orderTimeWeekend, "llr_brandXordWknd" = llr) %>% arrange(brand)
  
  ggplot(data=llr_brandXordWknd,aes(x=brand, y=orderTimeWeekend, size = llr_brandXordWknd),alpha=.1) + geom_point()
  qplot(brand,llr_brandXordWknd,data=llr_brandXordWknd, geom='line', group=orderTimeWeekend, facets = orderTimeWeekend ~ .)

  TVC %>% left_join(llr_brandXordWknd, by=c("brand","orderTimeWeekend")) %>%
     select(orderID,brand,dsn,orderTimeWeekend,llr_brandXordWknd,couponUsed) %>%
     ggplot(aes(x=orderTimeWeekend,y=llr_brandXordWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_brandXordWknd = TVC %>% 
     left_join(llr_brandXordWknd, by=c("brand","orderTimeWeekend")) %>%
     select(orderID,dsn,llr_brandXordWknd)

   trn = llr_brandXordWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_brandXordWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_brandXordWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_brandXordWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brandXordWknd,"../features/feature_files/llr_brandXordWknd.rds")
```

*productGroup* (as `llr_brandXprod`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # productGroup 
  llr = compute_ll_2w(as.character(H$brand), as.character(H$productGroup), H$couponUsed, as.character(TVC$brand), as.character(TVC$productGroup))
  llr_brandXprod = data.frame("brand" = TVC$brand, "productGroup" = TVC$productGroup, "llr_brandXprod" = llr) %>% arrange(brand)
  
  ggplot(data=llr_brandXprod,aes(x=brand, y=productGroup, size = llr_brandXprod),alpha=.1) + geom_point()
  qplot(brand,llr_brandXprod,data=llr_brandXprod, geom='line', group=productGroup, facets = productGroup ~ .)

  TVC %>% left_join(llr_brandXprod, by=c("brand","productGroup")) %>%
     select(orderID,brand,dsn,productGroup,llr_brandXprod,couponUsed) %>%
     ggplot(aes(x=productGroup,y=llr_brandXprod,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_brandXprod = TVC %>% 
     left_join(llr_brandXprod, by=c("brand","productGroup")) %>%
     select(orderID,dsn,llr_brandXprod)

   trn = llr_brandXprod %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_brandXprod %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_brandXprod %>% filter(dsn == "class") %>% select(-dsn)

   llr_brandXprod = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brandXprod,"../features/feature_files/llr_brandXprod.rds")
```

*couponCol* (as `llr_brandXcpncol`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponCol 
  llr = compute_ll_2w(as.character(H$brand), as.character(H$couponCol), H$couponUsed, as.character(TVC$brand), as.character(TVC$couponCol))
  llr_brandXcpncol = data.frame("brand" = TVC$brand, "couponCol" = TVC$couponCol, "llr_brandXcpncol" = llr) %>% arrange(brand)
  
  ggplot(data=llr_brandXcpncol,aes(x=brand, y=couponCol, size = llr_brandXcpncol),alpha=.1) + geom_point()
  qplot(brand,llr_brandXcpncol,data=llr_brandXcpncol, geom='line', group=couponCol, facets = couponCol ~ .)

  TVC %>% left_join(llr_brandXcpncol, by=c("brand","couponCol")) %>%
     select(orderID,brand,dsn,couponCol,llr_brandXcpncol,couponUsed) %>%
     ggplot(aes(x=couponCol,y=llr_brandXcpncol,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_brandXcpncol = TVC %>% 
     left_join(llr_brandXcpncol, by=c("brand","couponCol")) %>%
     select(orderID,dsn,llr_brandXcpncol)

   trn = llr_brandXcpncol %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_brandXcpncol %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_brandXcpncol %>% filter(dsn == "class") %>% select(-dsn)

   llr_brandXcpncol = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_brandXcpncol,"../features/feature_files/llr_brandXcpncol.rds")
```

## productGroup and 
*couponsReceivedDoW* (as `llr_prodXrecDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedDoW 
  llr = compute_ll_2w(as.character(H$productGroup), as.character(H$couponsReceivedDoW), H$couponUsed, as.character(TVC$productGroup), as.character(TVC$couponsReceivedDoW))
  llr_prodXrecDoW = data.frame("productGroup" = TVC$productGroup, "couponsReceivedDoW" = TVC$couponsReceivedDoW, "llr_prodXrecDoW" = llr) %>% arrange(productGroup)
  
  ggplot(data=llr_prodXrecDoW,aes(x=productGroup, y=couponsReceivedDoW, size = llr_prodXrecDoW),alpha=.1) + geom_point()
  qplot(productGroup,llr_prodXrecDoW,data=llr_prodXrecDoW, geom='line', group=couponsReceivedDoW, facets = couponsReceivedDoW ~ .)

  TVC %>% left_join(llr_prodXrecDoW, by=c("productGroup","couponsReceivedDoW")) %>%
     select(orderID,productGroup,dsn,couponsReceivedDoW,llr_prodXrecDoW,couponUsed) %>%
     ggplot(aes(x=couponsReceivedDoW,y=llr_prodXrecDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_prodXrecDoW = TVC %>% 
     left_join(llr_prodXrecDoW, by=c("productGroup","couponsReceivedDoW")) %>%
     select(orderID,dsn,llr_prodXrecDoW)

   trn = llr_prodXrecDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_prodXrecDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_prodXrecDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_prodXrecDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_prodXrecDoW,"../features/feature_files/llr_prodXrecDoW.rds")
```

*couponsReceivedFriSat* (as `llr_prodXrecFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedFriSat 
  llr = compute_ll_2w(as.character(H$productGroup), as.character(H$couponsReceivedFriSat), H$couponUsed, as.character(TVC$productGroup), as.character(TVC$couponsReceivedFriSat))
  llr_prodXrecFS = data.frame("productGroup" = TVC$productGroup, "couponsReceivedFriSat" = TVC$couponsReceivedFriSat, "llr_prodXrecFS" = llr) %>% arrange(productGroup)
  
  ggplot(data=llr_prodXrecFS,aes(x=productGroup, y=couponsReceivedFriSat, size = llr_prodXrecFS),alpha=.1) + geom_point()
  qplot(productGroup,llr_prodXrecFS,data=llr_prodXrecFS, geom='line', group=couponsReceivedFriSat, facets = couponsReceivedFriSat ~ .)

  TVC %>% left_join(llr_prodXrecFS, by=c("productGroup","couponsReceivedFriSat")) %>%
     select(orderID,productGroup,dsn,couponsReceivedFriSat,llr_prodXrecFS,couponUsed) %>%
     ggplot(aes(x=couponsReceivedFriSat,y=llr_prodXrecFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_prodXrecFS = TVC %>% 
     left_join(llr_prodXrecFS, by=c("productGroup","couponsReceivedFriSat")) %>%
     select(orderID,dsn,llr_prodXrecFS)

   trn = llr_prodXrecFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_prodXrecFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_prodXrecFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_prodXrecFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_prodXrecFS,"../features/feature_files/llr_prodXrecFS.rds")
```

*couponsReceivedWeekend* (as `llr_prodXrecWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedWeekend 
  llr = compute_ll_2w(as.character(H$productGroup), as.character(H$couponsReceivedWeekend), H$couponUsed, as.character(TVC$productGroup), as.character(TVC$couponsReceivedWeekend))
  llr_prodXrecWknd = data.frame("productGroup" = TVC$productGroup, "couponsReceivedWeekend" = TVC$couponsReceivedWeekend, "llr_prodXrecWknd" = llr) %>% arrange(productGroup)
  
  ggplot(data=llr_prodXrecWknd,aes(x=productGroup, y=couponsReceivedWeekend, size = llr_prodXrecWknd),alpha=.1) + geom_point()
  qplot(productGroup,llr_prodXrecWknd,data=llr_prodXrecWknd, geom='line', group=couponsReceivedWeekend, facets = couponsReceivedWeekend ~ .)

  TVC %>% left_join(llr_prodXrecWknd, by=c("productGroup","couponsReceivedWeekend")) %>%
     select(orderID,productGroup,dsn,couponsReceivedWeekend,llr_prodXrecWknd,couponUsed) %>%
     ggplot(aes(x=couponsReceivedWeekend,y=llr_prodXrecWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_prodXrecWknd = TVC %>% 
     left_join(llr_prodXrecWknd, by=c("productGroup","couponsReceivedWeekend")) %>%
     select(orderID,dsn,llr_prodXrecWknd)

   trn = llr_prodXrecWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_prodXrecWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_prodXrecWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_prodXrecWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_prodXrecWknd,"../features/feature_files/llr_prodXrecWknd.rds")
```

*orderTimeDoW* (as `llr_prodXordDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeDoW 
  llr = compute_ll_2w(as.character(H$productGroup), as.character(H$orderTimeDoW), H$couponUsed, as.character(TVC$productGroup), as.character(TVC$orderTimeDoW))
  llr_prodXordDoW = data.frame("productGroup" = TVC$productGroup, "orderTimeDoW" = TVC$orderTimeDoW, "llr_prodXordDoW" = llr) %>% arrange(productGroup)
  
  ggplot(data=llr_prodXordDoW,aes(x=productGroup, y=orderTimeDoW, size = llr_prodXordDoW),alpha=.1) + geom_point()
  qplot(productGroup,llr_prodXordDoW,data=llr_prodXordDoW, geom='line', group=orderTimeDoW, facets = orderTimeDoW ~ .)

  TVC %>% left_join(llr_prodXordDoW, by=c("productGroup","orderTimeDoW")) %>%
     select(orderID,productGroup,dsn,orderTimeDoW,llr_prodXordDoW,couponUsed) %>%
     ggplot(aes(x=orderTimeDoW,y=llr_prodXordDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_prodXordDoW = TVC %>% 
     left_join(llr_prodXordDoW, by=c("productGroup","orderTimeDoW")) %>%
     select(orderID,dsn,llr_prodXordDoW)

   trn = llr_prodXordDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_prodXordDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_prodXordDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_prodXordDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_prodXordDoW,"../features/feature_files/llr_prodXordDoW.rds")
```

*orderTimeFriSat* (as `llr_prodXordFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeFriSat 
  llr = compute_ll_2w(as.character(H$productGroup), as.character(H$orderTimeFriSat), H$couponUsed, as.character(TVC$productGroup), as.character(TVC$orderTimeFriSat))
  llr_prodXordFS = data.frame("productGroup" = TVC$productGroup, "orderTimeFriSat" = TVC$orderTimeFriSat, "llr_prodXordFS" = llr) %>% arrange(productGroup)
  
  ggplot(data=llr_prodXordFS,aes(x=productGroup, y=orderTimeFriSat, size = llr_prodXordFS),alpha=.1) + geom_point()
  qplot(productGroup,llr_prodXordFS,data=llr_prodXordFS, geom='line', group=orderTimeFriSat, facets = orderTimeFriSat ~ .)

  TVC %>% left_join(llr_prodXordFS, by=c("productGroup","orderTimeFriSat")) %>%
     select(orderID,productGroup,dsn,orderTimeFriSat,llr_prodXordFS,couponUsed) %>%
     ggplot(aes(x=orderTimeFriSat,y=llr_prodXordFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_prodXordFS = TVC %>% 
     left_join(llr_prodXordFS, by=c("productGroup","orderTimeFriSat")) %>%
     select(orderID,dsn,llr_prodXordFS)

   trn = llr_prodXordFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_prodXordFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_prodXordFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_prodXordFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_prodXordFS,"../features/feature_files/llr_prodXordFS.rds")
```

*orderTimeWeekend* (as `llr_prodXordWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeWeekend 
  llr = compute_ll_2w(as.character(H$productGroup), as.character(H$orderTimeWeekend), H$couponUsed, as.character(TVC$productGroup), as.character(TVC$orderTimeWeekend))
  llr_prodXordWknd = data.frame("productGroup" = TVC$productGroup, "orderTimeWeekend" = TVC$orderTimeWeekend, "llr_prodXordWknd" = llr) %>% arrange(productGroup)
  
  ggplot(data=llr_prodXordWknd,aes(x=productGroup, y=orderTimeWeekend, size = llr_prodXordWknd),alpha=.1) + geom_point()
  qplot(productGroup,llr_prodXordWknd,data=llr_prodXordWknd, geom='line', group=orderTimeWeekend, facets = orderTimeWeekend ~ .)

  TVC %>% left_join(llr_prodXordWknd, by=c("productGroup","orderTimeWeekend")) %>%
     select(orderID,productGroup,dsn,orderTimeWeekend,llr_prodXordWknd,couponUsed) %>%
     ggplot(aes(x=orderTimeWeekend,y=llr_prodXordWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_prodXordWknd = TVC %>% 
     left_join(llr_prodXordWknd, by=c("productGroup","orderTimeWeekend")) %>%
     select(orderID,dsn,llr_prodXordWknd)

   trn = llr_prodXordWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_prodXordWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_prodXordWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_prodXordWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_prodXordWknd,"../features/feature_files/llr_prodXordWknd.rds")
```

*couponCol* (as `llr_prodXcpncol`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponCol 
  llr = compute_ll_2w(as.character(H$productGroup), as.character(H$couponCol), H$couponUsed, as.character(TVC$productGroup), as.character(TVC$couponCol))
  llr_prodXcpncol = data.frame("productGroup" = TVC$productGroup, "couponCol" = TVC$couponCol, "llr_prodXcpncol" = llr) %>% arrange(productGroup)
  
  ggplot(data=llr_prodXcpncol,aes(x=productGroup, y=couponCol, size = llr_prodXcpncol),alpha=.1) + geom_point()
  qplot(productGroup,llr_prodXcpncol,data=llr_prodXcpncol, geom='line', group=couponCol, facets = couponCol ~ .)

  TVC %>% left_join(llr_prodXcpncol, by=c("productGroup","couponCol")) %>%
     select(orderID,productGroup,dsn,couponCol,llr_prodXcpncol,couponUsed) %>%
     ggplot(aes(x=couponCol,y=llr_prodXcpncol,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_prodXcpncol = TVC %>% 
     left_join(llr_prodXcpncol, by=c("productGroup","couponCol")) %>%
     select(orderID,dsn,llr_prodXcpncol)

   trn = llr_prodXcpncol %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_prodXcpncol %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_prodXcpncol %>% filter(dsn == "class") %>% select(-dsn)

   llr_prodXcpncol = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_prodXcpncol,"../features/feature_files/llr_prodXcpncol.rds")
```

## couponID and 
*couponsReceivedDoW* (as `llr_cpnXrecDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedDoW 
  llr = compute_ll_2w(as.character(H$couponID), as.character(H$couponsReceivedDoW), H$couponUsed, as.character(TVC$couponID), as.character(TVC$couponsReceivedDoW))
  llr_cpnXrecDoW = data.frame("couponID" = TVC$couponID, "couponsReceivedDoW" = TVC$couponsReceivedDoW, "llr_cpnXrecDoW" = llr) %>% arrange(couponID)
  
  ggplot(data=llr_cpnXrecDoW,aes(x=couponID, y=couponsReceivedDoW, size = llr_cpnXrecDoW),alpha=.1) + geom_point()
  qplot(couponID,llr_cpnXrecDoW,data=llr_cpnXrecDoW, geom='line', group=couponsReceivedDoW, facets = couponsReceivedDoW ~ .)

  TVC %>% left_join(llr_cpnXrecDoW, by=c("couponID","couponsReceivedDoW")) %>%
     select(orderID,couponID,dsn,couponsReceivedDoW,llr_cpnXrecDoW,couponUsed) %>%
     ggplot(aes(x=couponsReceivedDoW,y=llr_cpnXrecDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_cpnXrecDoW = TVC %>% 
     left_join(llr_cpnXrecDoW, by=c("couponID","couponsReceivedDoW")) %>%
     select(orderID,dsn,llr_cpnXrecDoW)

   trn = llr_cpnXrecDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_cpnXrecDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_cpnXrecDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_cpnXrecDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_cpnXrecDoW,"../features/feature_files/llr_cpnXrecDoW.rds")
```

*couponsReceivedFriSat* (as `llr_cpnXrecFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedFriSat 
  llr = compute_ll_2w(as.character(H$couponID), as.character(H$couponsReceivedFriSat), H$couponUsed, as.character(TVC$couponID), as.character(TVC$couponsReceivedFriSat))
  llr_cpnXrecFS = data.frame("couponID" = TVC$couponID, "couponsReceivedFriSat" = TVC$couponsReceivedFriSat, "llr_cpnXrecFS" = llr) %>% arrange(couponID)
  
  ggplot(data=llr_cpnXrecFS,aes(x=couponID, y=couponsReceivedFriSat, size = llr_cpnXrecFS),alpha=.1) + geom_point()
  qplot(couponID,llr_cpnXrecFS,data=llr_cpnXrecFS, geom='line', group=couponsReceivedFriSat, facets = couponsReceivedFriSat ~ .)

  TVC %>% left_join(llr_cpnXrecFS, by=c("couponID","couponsReceivedFriSat")) %>%
     select(orderID,couponID,dsn,couponsReceivedFriSat,llr_cpnXrecFS,couponUsed) %>%
     ggplot(aes(x=couponsReceivedFriSat,y=llr_cpnXrecFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_cpnXrecFS = TVC %>% 
     left_join(llr_cpnXrecFS, by=c("couponID","couponsReceivedFriSat")) %>%
     select(orderID,dsn,llr_cpnXrecFS)

   trn = llr_cpnXrecFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_cpnXrecFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_cpnXrecFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_cpnXrecFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_cpnXrecFS,"../features/feature_files/llr_cpnXrecFS.rds")
```

*couponsReceivedWeekend* (as `llr_cpnXrecWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponsReceivedWeekend 
  llr = compute_ll_2w(as.character(H$couponID), as.character(H$couponsReceivedWeekend), H$couponUsed, as.character(TVC$couponID), as.character(TVC$couponsReceivedWeekend))
  llr_cpnXrecWknd = data.frame("couponID" = TVC$couponID, "couponsReceivedWeekend" = TVC$couponsReceivedWeekend, "llr_cpnXrecWknd" = llr) %>% arrange(couponID)
  
  ggplot(data=llr_cpnXrecWknd,aes(x=couponID, y=couponsReceivedWeekend, size = llr_cpnXrecWknd),alpha=.1) + geom_point()
  qplot(couponID,llr_cpnXrecWknd,data=llr_cpnXrecWknd, geom='line', group=couponsReceivedWeekend, facets = couponsReceivedWeekend ~ .)

  TVC %>% left_join(llr_cpnXrecWknd, by=c("couponID","couponsReceivedWeekend")) %>%
     select(orderID,couponID,dsn,couponsReceivedWeekend,llr_cpnXrecWknd,couponUsed) %>%
     ggplot(aes(x=couponsReceivedWeekend,y=llr_cpnXrecWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_cpnXrecWknd = TVC %>% 
     left_join(llr_cpnXrecWknd, by=c("couponID","couponsReceivedWeekend")) %>%
     select(orderID,dsn,llr_cpnXrecWknd)

   trn = llr_cpnXrecWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_cpnXrecWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_cpnXrecWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_cpnXrecWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_cpnXrecWknd,"../features/feature_files/llr_cpnXrecWknd.rds")
```

*orderTimeDoW* (as `llr_cpnXordDoW`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeDoW 
  llr = compute_ll_2w(as.character(H$couponID), as.character(H$orderTimeDoW), H$couponUsed, as.character(TVC$couponID), as.character(TVC$orderTimeDoW))
  llr_cpnXordDoW = data.frame("couponID" = TVC$couponID, "orderTimeDoW" = TVC$orderTimeDoW, "llr_cpnXordDoW" = llr) %>% arrange(couponID)
  
  ggplot(data=llr_cpnXordDoW,aes(x=couponID, y=orderTimeDoW, size = llr_cpnXordDoW),alpha=.1) + geom_point()
  qplot(couponID,llr_cpnXordDoW,data=llr_cpnXordDoW, geom='line', group=orderTimeDoW, facets = orderTimeDoW ~ .)

  TVC %>% left_join(llr_cpnXordDoW, by=c("couponID","orderTimeDoW")) %>%
     select(orderID,couponID,dsn,orderTimeDoW,llr_cpnXordDoW,couponUsed) %>%
     ggplot(aes(x=orderTimeDoW,y=llr_cpnXordDoW,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_cpnXordDoW = TVC %>% 
     left_join(llr_cpnXordDoW, by=c("couponID","orderTimeDoW")) %>%
     select(orderID,dsn,llr_cpnXordDoW)

   trn = llr_cpnXordDoW %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_cpnXordDoW %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_cpnXordDoW %>% filter(dsn == "class") %>% select(-dsn)

   llr_cpnXordDoW = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_cpnXordDoW,"../features/feature_files/llr_cpnXordDoW.rds")
```

*orderTimeFriSat* (as `llr_cpnXordFS`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeFriSat 
  llr = compute_ll_2w(as.character(H$couponID), as.character(H$orderTimeFriSat), H$couponUsed, as.character(TVC$couponID), as.character(TVC$orderTimeFriSat))
  llr_cpnXordFS = data.frame("couponID" = TVC$couponID, "orderTimeFriSat" = TVC$orderTimeFriSat, "llr_cpnXordFS" = llr) %>% arrange(couponID)
  
  ggplot(data=llr_cpnXordFS,aes(x=couponID, y=orderTimeFriSat, size = llr_cpnXordFS),alpha=.1) + geom_point()
  qplot(couponID,llr_cpnXordFS,data=llr_cpnXordFS, geom='line', group=orderTimeFriSat, facets = orderTimeFriSat ~ .)

  TVC %>% left_join(llr_cpnXordFS, by=c("couponID","orderTimeFriSat")) %>%
     select(orderID,couponID,dsn,orderTimeFriSat,llr_cpnXordFS,couponUsed) %>%
     ggplot(aes(x=orderTimeFriSat,y=llr_cpnXordFS,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_cpnXordFS = TVC %>% 
     left_join(llr_cpnXordFS, by=c("couponID","orderTimeFriSat")) %>%
     select(orderID,dsn,llr_cpnXordFS)

   trn = llr_cpnXordFS %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_cpnXordFS %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_cpnXordFS %>% filter(dsn == "class") %>% select(-dsn)

   llr_cpnXordFS = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_cpnXordFS,"../features/feature_files/llr_cpnXordFS.rds")
```

*orderTimeWeekend* (as `llr_cpnXordWknd`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # orderTimeWeekend 
  llr = compute_ll_2w(as.character(H$couponID), as.character(H$orderTimeWeekend), H$couponUsed, as.character(TVC$couponID), as.character(TVC$orderTimeWeekend))
  llr_cpnXordWknd = data.frame("couponID" = TVC$couponID, "orderTimeWeekend" = TVC$orderTimeWeekend, "llr_cpnXordWknd" = llr) %>% arrange(couponID)
  
  ggplot(data=llr_cpnXordWknd,aes(x=couponID, y=orderTimeWeekend, size = llr_cpnXordWknd),alpha=.1) + geom_point()
  qplot(couponID,llr_cpnXordWknd,data=llr_cpnXordWknd, geom='line', group=orderTimeWeekend, facets = orderTimeWeekend ~ .)

  TVC %>% left_join(llr_cpnXordWknd, by=c("couponID","orderTimeWeekend")) %>%
     select(orderID,couponID,dsn,orderTimeWeekend,llr_cpnXordWknd,couponUsed) %>%
     ggplot(aes(x=orderTimeWeekend,y=llr_cpnXordWknd,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_cpnXordWknd = TVC %>% 
     left_join(llr_cpnXordWknd, by=c("couponID","orderTimeWeekend")) %>%
     select(orderID,dsn,llr_cpnXordWknd)

   trn = llr_cpnXordWknd %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_cpnXordWknd %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_cpnXordWknd %>% filter(dsn == "class") %>% select(-dsn)

   llr_cpnXordWknd = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_cpnXordWknd,"../features/feature_files/llr_cpnXordWknd.rds")
```

*couponCol* (as `llr_cpnXcpncol`)
<!--- userid2ways: R code (No Results in Document) -->
```{r cache=TRUE}
  # couponCol 
  llr = compute_ll_2w(as.character(H$couponID), as.character(H$couponCol), H$couponUsed, as.character(TVC$couponID), as.character(TVC$couponCol))
  llr_cpnXcpncol = data.frame("couponID" = TVC$couponID, "couponCol" = TVC$couponCol, "llr_cpnXcpncol" = llr) %>% arrange(couponID)
  
  ggplot(data=llr_cpnXcpncol,aes(x=couponID, y=couponCol, size = llr_cpnXcpncol),alpha=.1) + geom_point()
  qplot(couponID,llr_cpnXcpncol,data=llr_cpnXcpncol, geom='line', group=couponCol, facets = couponCol ~ .)

  TVC %>% left_join(llr_cpnXcpncol, by=c("couponID","couponCol")) %>%
     select(orderID,couponID,dsn,couponCol,llr_cpnXcpncol,couponUsed) %>%
     ggplot(aes(x=couponCol,y=llr_cpnXcpncol,fill=factor(couponUsed),color=dsn))+geom_boxplot()+facet_grid(dsn~.)

  llr_cpnXcpncol = TVC %>% 
     left_join(llr_cpnXcpncol, by=c("couponID","couponCol")) %>%
     select(orderID,dsn,llr_cpnXcpncol)

   trn = llr_cpnXcpncol %>% filter(dsn == "train") %>% select(-dsn)
   val = llr_cpnXcpncol %>% filter(dsn == "validation") %>% select(-dsn)
   cls = llr_cpnXcpncol %>% filter(dsn == "class") %>% select(-dsn)

   llr_cpnXcpncol = list("T" = trn, "V" = val, "C" = cls) 

   saveRDS(llr_cpnXcpncol,"../features/feature_files/llr_cpnXcpncol.rds")
```

