---
title: Creating better LLRs
titleshort: We can maybe get these for 
instructions: 
output:
  usefulR::DMC_format
---

<!--- # (R code (No Results in Document)) -->
```{r set-parent, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   #set up knitr
   #devtools::install_github('imouzon/usefulR')
   library(usefulR)

   #set working directory
   working.dir = "/Users/user/dmc2015/ian"
   setwd(working.dir)

   #compile the document to PDF
   if(FALSE) 
      rmarkdown::render("/Users/user/dmc2015/ian/multiway_llr_set1.rmd")
```

I am using the following packages:
<!--- # (R code (No Results in Document))-->
```{r paks, echo=TRUE, cache=FALSE, message=FALSE, tidy=FALSE, include=TRUE}
   library(magrittr)
   library(dplyr)
   library(reshape2)
   library(tidyr)
   library(lubridate)
   library(ggplot2)
   library(directlabels)
   library(rCharts)
   library(xtable)
   library(foreach)
   library(gtools)
   library(knitr)
   library(utils)
   source("~/dmc2015/ian/R/renm.R")
```
My working directory is set to \verb!~/dmc2015/ian/!.

# Bayesian Basket Values
I am using our new clean data - so should you
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
   d = readRDS("../data/clean_data/universalCleanData.rds")

   source("./R/clean_factor.r")
   d = clean_factor(d,"couponID","cpn")
   d = clean_factor(d,"brand","brand")
   d = clean_factor(d,"productGroup","prod")
   d = clean_factor(d,"categoryIDs")
```

I can melt the columns by coupon using the following:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   source("./r/stackCoupons2.R")
   dm = stackCoupons2(d,idcols = c(1:4,32:49)) 
```

## Make a few quick features
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   dm$ShopFast = 1*(dm$TimeBtwnRecOrder < 28)
   dm$EarlyRec = 1*(dm$TimeBtwnSentRec < 8)

   dm$Shop60 = floor(dm$orderTimeTime)
   dm$Shop30 = floor(dm$orderTimeTime * 60/30)*30/60
   dm$Shop15 = floor(dm$orderTimeTime * 60/15)*15/60

   dm$RecExpire60 = floor(dm$TimeBtwnSentRec)
   dm$RecOrder60 = floor(dm$TimeBtwnRecOrder)
   dm$OrderExpire60 = floor(dm$TimeBtwnOrderExpire)
   dm$basePrice_price_ratio = dm$basePrice/dm$price
```

I and can split the columns of product group using:
<!--- splitcols: R code (No Results in Document) -->
```{r splitcols,cache=FALSE}
   source("./r/splitColumn.R")
   dmc = splitColumn(dm,"categoryIDs","orderID",splitby=":") 
   dmc = dmc[,-which(names(dmc) == "categoryIDs")]
   dmc = clean_factor(dmc,"categoryIDs",scrape_off="cat")
   dmc = dm %>% 
      left_join(dmc %>%
            select(orderID,couponCol,categoryIDs1, categoryIDs2, categoryIDs3, categoryIDs4, categoryIDs5) %>%
            gather(tmp,categoryID,-orderID,-couponCol) %>%
            mutate(categoryEntry = gsub("categoryIDs","",tmp)) %>%
            select(orderID,couponCol,categoryEntry,categoryID) %>%
            arrange(orderID,couponCol,categoryEntry) %>%
            filter(!is.na(categoryID)),
         by = c("orderID","couponCol")) %>%
      arrange(orderID,couponCol,categoryEntry)
```

## Based on Historical Set 1
<!--- readHist1: R code (No Results in Document) -->
```{r readHist1,cache=FALSE}
   HTVset1 = readRDS("~/dmc2015/data/featureMatrix/HTVset3.rds")
   names(dm)
```

#basket Bayes
Consider the (trimmed) density of basketValue:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   d.tmp = d %>% mutate(couponUse = paste0(coupon1Used,coupon2Used,coupon3Used))
   qplot(basketValue,xlim=c(0,1000),binwidth=3,data=d.tmp,color=couponUse)

   qplot(floor(basketValue/10),xlim=c(0,200),binwidth=1,data=d.tmp,color=couponUse)

   d.tmp %>% mutate(newval= floor(basketValue/10)) %>% group_by(newval) %>% summarize(freq = n()) %>% arrange(-freq) %>% head(10)
   d.tmp %>% mutate(newval= floor(basketValue/10)) %>% filter(newval == 18) %>% group_by(basketValue) %>% summarize(freq = n()) %>% arrange(-freq) %>% head(10)

   plot.d = d.tmp %>% mutate(basketGroup = (1*(basketValue > 185) + 
                                         1*(basketValue > 137) +
                                         1*(basketValue > 92)),newval= as.character(floor(basketValue/10)),
                             couponsUsed = (1*(coupon1Used == 1) + 
                                            1*(coupon2Used == 1) + 
                                            1*(coupon3Used == 1)))

   ## these plots illustrate the distribution
   qplot(basketValue,xlim=c(0,1000),binwidth=1,data=plot.d,fill=factor(basketGroup))
   qplot(basketValue,xlim=c(0,1000),binwidth=1,data=plot.d,facets=couponsUsed~.,fill=factor(basketGroup))

   ## add this grouping to the data
   d = d %>% mutate(basketGroup = (1*(basketValue > 185) + 1*(basketValue > 137) + 1*(basketValue > 92)))
   dm = dm %>% mutate(basketGroup = (1*(basketValue > 185) + 1*(basketValue > 137) + 1*(basketValue > 92))) %>% head
```

<!--- chunk-label: R code (No Results in Document) -->
```{r diffbygroup,cache=FALSE}
   ## behavior by categorical data
   bygroupPlot = function(catvar,dsn=d){
      dsn$catvar = sapply(1:nrow(dsn), function(i) paste0(sapply(catvar, function(x) as.character(dsn[i,x])),collapse=":"))
      dsn = dsn[,c("basketGroup","catvar")]
      p = dsn %>% group_by(basketGroup,catvar) %>% 
         mutate(catXgroup_freq=n()) %>%
         group_by(basketGroup) %>% 
         mutate(cat_in_group_prop = catXgroup_freq/n()) %>%
         unique %>%
         arrange(basketGroup,catvar) %>%
         ggplot(aes(factor(basketGroup),catvar,size=cat_in_group_prop,color=factor(catvar)))+geom_point()
      return(p)
   }
```

<!--- chunk-label: R code (No Results in Document) -->
```{r chunk-label,cache=FALSE}
   bygroupPlot(c("coupon1Used","coupon2Used","coupon3Used"))
   bygroupPlot(c("userID"))
```

<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   dtmp = d
   dtmp$cash185 = c("cash185","no")[(dtmp$basketValue < 186 & dtmp$basketValue > 185) + 1]
   dtmp %>% filter(!is.na(cash185)) %>% group_by(cash185,couponID1) %>% summarize(prop = sum(coupon1Used)/n()) %>%  arrange(cash185,-prop)
   qplot(couponsReceived,orderTime,facets=reward1~cash185,alpha=I(1),data=dtmp) 
```


## She's Losing It: Bayesian Expectation
From the form of our loss function on basketValues, we know that the **best** estimator, 
the one that minimizes our expected loss function for some given feature values $x_1, x_2, ..., x_p$, 
is going to be the expected basket value based on those features, i.e., to minimize
$$
   \mathbb{E} \left( (b_i - \hat{b}_i)^2 | x_{1,i}, x_{2,i}, ..., x_{p,i} \right)
$$
is 
$$
\mathbb{E} \left( \hat{b}_i | x_{1,i}, x_{2,i}, ..., x_{p,i} \right)
$$
Since we don't know 
$
\mathbb{E} \left( \hat{b}_i | x_{1,i}, x_{2,i}, ..., x_{p,i} \right)
$
our best bet minimize our expected loss on basketValue is to estimate that loss.
We can do this in the same way we used our historical data to estimate coupon use.

Consider for a given user, $u_i$, with basketValues $b_1$, $b_2$, ..., $b_k$ 
and believe the following: 
\begin{align}
b_i          &\sim f(b | \theta_{u_i} ) \tag{data model} \\
\theta_{u_i} &\sim \pi(\theta) \tag{prior} \\
\end{align}
we can say that seeing $b_1, b_2, ..., b_k$ has updated our "prior" belief about $\theta$'s distribution.
If we can connect that updated (posterior) estimate of $\theta$ to $\mathbb{E}(b | u_i)$ (for instance if 
$\theta$ represents the mean of $b$ for user $u_i$), 
then we have an aspect of the estimate we are looking for.

We can do this for multiple combinations of these features. 
Notice that the basket values have some sort of "mixed" exponential distribution. We can consider
the mixed exponential as have the following mixing proportions (estiamted on the entire data):
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   d %>% filter(!is.na(basketValue)) %>% group_by(basketGroup) %>% summarize(pi_est = n()/nrow(d))
```
so we have $\pi_1 = 0.00193$, $\pi_2 = 0.084747$, $\pi_3 = 0.09119$, and $\pi_4 = 0.7199$.
Also we can consider a very rough estimate of each curve using the following:

$$
x \sim 
\begin{cases}
\lambda_1 e ^ {-\lambda_1 (x - 185) & x \ge 185 \\
\lambda_2 e ^ {-\lambda_2 (x - 137) & x \ge 185 \\
\lambda_3 e ^ {-\lambda_3 (x - 92) & x \ge 185 \\
\lambda_4 e ^ {-\lambda_4 (x - 185) & x \ge 185 \\
\end{cases}
$$
If we conisder a customers basketValues as being draws from some unknown disprior unkn 
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   alpha.est = 24
   beta.est = 4*alpha.est 
   qbeta(.025,alpha.est,beta.est)
   qbeta(.975,alpha.est,beta.est)
```
This means that we can get posterior estimates of the per column probability using the following:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   p1 = (sum(HTVset1$H$coupon1Used) + alpha.est)/(nrow(HTVset1$H) + alpha.est + beta.est)
   p2 = (sum(HTVset1$H$coupon2Used) + alpha.est)/(nrow(HTVset1$H) + alpha.est + beta.est)
   p3 = (sum(HTVset1$H$coupon3Used) + alpha.est)/(nrow(HTVset1$H) + alpha.est + beta.est)
```
And we can weight our observations using these proportions:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
yrf = 
   

```







## Making comparisons
Using these likelihoods, we can make the following comparisons:
**basePrice_price_ratio, reward**
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   colsel = which(names(dm) %in% c("basePrice_price_ratio","reward"))
   result = llr_multiway(dm,HTVset1$H,colsel)

   dm %>% left_join(result$long, by= c("orderID","couponCol")) %>% ggplot(aes(factor(reward),llr_naive_rwdXbasePrice_price_ratio,color=factor(couponUsed),group=couponCol)) + geom_boxplot()

   #show long results
   tail(result$long) %>% kable

   #show wide results
   head(result$wide) %>% kable
```

Make this a function:
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
CreateSets = function(varns){
   filename = paste(varns,collapse="X")
   colsel = which(names(dm) %in% varns)

   message("Now making llrs for ",filename)
   result = llr_multiway(dm,HTVset1$H,colsel)

   #save long results
   result$long %>% saveRDS(file = paste0("~/dmc2015/features/feature_files/set1/llr_",filename,"_long.rds"))

   #save wide results
   result$wide %>% saveRDS(file = paste0("~/dmc2015/features/feature_files/set1/llr_",filename,"_wide.rds"))
}
```

## Choosing comparisons

<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
#comparison groups
groupA = c("Shop60", "Shop30", "Shop15", "RecExpire60", "RecOrder60", "OrderExpire60")

groupB = c("basePrice_price_ratio", "price", "basePrice")

groupC1 = "userID"
groupC2 = "couponID"

groupD1 = c("ShopFast", "EarlyRec")
groupD2 = c("premiumProduct", "brand", "productGroup", "categoryIDs","reward")
```


# One way Comparisons
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
# one way
oneway = c(groupA,groupB,groupC1,groupC2,groupD1,groupD2)
sapply(oneway, function(i) CreateSets(i)) 
```


# Two Way Comparisons
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
## two way
twoway = combn(c(groupC1,groupB,groupD1,groupD2),2) %>% 
         cbind(combn(c(groupC1,groupC2),2)) %>%           # group C is OK for internal 2 way
         cbind(combn(c(groupC2,groupD1),2))               # group D is OK for internal 2 way

sapply(1:ncol(twoway), function(i) CreateSets(twoway[,i]))
```


# Three Way Comparisons
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
## three way 
threeway = combn(c(groupB,groupC1),3) %>%                                                     # group B = 2 and userID is OK 
   cbind(do.call("cbind", lapply(groupB, function(x) combn(c(x,groupD1,groupD2),3)))) %>%      # group B = 1 and group D = 2 is OK
   cbind(do.call("cbind",lapply(c(groupD1,groupD2), function(x) combn(c(x,groupB),3)))) %>%   # group B = 2 and group D = 1 is OK
   cbind(combn(c(groupC1,groupD1,groupD2),3))

sapply(1:ncol(threeway), function(i) CreateSets(threeway[,i]))
```


# Four Way Comparisons
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
## four way
fourway = combn(c(groupD1,groupD2),4)
sapply(1:ncol(fourway), function(i) CreateSets(fourway[,i]))
```


# Five Way Comparisons
<!--- chunk-label: R code (No Results in Document) -->
```{r cache=FALSE}
## five way only for groupD and internal
fiveway = combn(c(groupD1,groupD2),5)
sapply(1:ncol(fiveway), function(i) CreateSets(fiveway[,i]))
```
