---
title: Curation and Cross Validation to Reduce Features
titleshort: Too many features
instructions: 
output:
  usefulR::DMC_format
---

<!--- # (R code (No Results in Document)) -->
```{r set-parent, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   #set up knitr
   #devtools::install_github('imouzon/usefulR')
   library(usefulR)

   #set working directory
   working.dir = "/Users/user/dmc2015/ian"
   setwd(working.dir)

   #compile the document to PDF
   if(FALSE) 
      rmarkdown::render("/Users/user/dmc2015/ian/PeteCheck.rmd")
```

I am using the following packages:
<!--- # (R code (No Results in Document))-->
```{r paks, echo=TRUE, cache=FALSE, message=FALSE, tidy=FALSE, include=TRUE}
   library(magrittr)
   library(dplyr)
   library(reshape2)
   library(tidyr)
   library(lubridate)
   library(ggplot2)
   library(directlabels)
   library(rCharts)
   library(xtable)
   library(foreach)
   library(gtools)
   library(knitr)
   library(utils)
   source("~/dmc2015/ian/R/renm.R")
```
My working directory is set to \verb!~/dmc2015/ian/!.

# Pete Check
Pete's in MN right now by he's soldiering through:

## Reading in Pete's Work

A few notes - there is definetly an interesting set of variables in this mix (particularly set 2's variables). 
I 
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   PeteImp = readRDS("../pete/predictions/importance.rds")

   ## 20 most important features in Set 1
   PeteImp %>% arrange(-h1_imp) %>% select(var,h1_imp) %>% head(10)

   ## 20 most important features in Set 2
   PeteImp %>% arrange(-h2_imp) %>% select(var,h2_imp) %>% head(10)

   ## 20 most important features in Set 3
   PeteImp %>% arrange(-h3_imp) %>% select(var,h3_imp) %>% head(10)
```

Alex is adapting these importance levels have been adapted to our variable selection set. Thanks Pete!

