---
title: 
titleshort:
instructions:
author: Ian Mouzon
authorshort: Mouzon
contact: imouzon@iastate.edu
grouplong: 
groupshort: 
leader: 
leadershort: 
semester: 
assignment: 
duedate: 
output:
  usefulR::hw_format
---

<!--- # (R code (No Results in Document)) -->
```{r set-parent, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,cache=TRUE,warning=FALSE,include=FALSE,comment=NA}
   #set up knitr
   #devtools::install_github('imouzon/usefulR')
   library(usefulR)

   #set working directory
   working.dir = '~/dmc2015/ian/'
   setwd(working.dir)

   #compile the document to PDF
   if(FALSE) 
      rmarkdown::render("train_and_validate.Rmd")
```

I am using the following packages to create this feature matrix:
<!--- packageLoad: R code (No Results in Document) -->
```{r packageLoad,cache=FALSE}
   library(ggplot2)
   library(lubridate)
   library(dplyr)
   library(reshape2)
   library(sqldf)
```

# Getting the data
I read the raw and clean data into R using the following simple commands:
<!--- readDat: R code (Code in Document) -->
```{r readDat, cache=FALSE}
   #training set ("historical data")
   d = readRDS("~/dmc2015/data/clean_data/clean_simple.rds")
```

## Adding Batch ID
The data set \verb!clean_simple! does not have batch information. 
I will have to add it in:
I read the batch ID file as follows:
%-- readBatch: R code (Code in Document)
<!--- batchIN: R code (No Results in Document) -->
```{r batchIN,cache=FALSE}
   #batch features in ~/dmc2015/features/feature_files/batchInfo_test.csv, batchInfo_train.csv
   bit = readRDS("~/dmc2015/features/feature_files/batchInfo_train.rds")
   bic = readRDS("~/dmc2015/features/feature_files/batchInfo_test.rds")
   bi = rbind(bit,bic)
```

Fix the formatting:
<!--- btchfromt: R code (No Results in Document) -->
```{r btchfromt,cache=FALSE}
   bi$couponsReceivedTime =  period_to_seconds(bi$couponsReceivedTime)/3600
   bi$orderTimeTime =  period_to_seconds(bi$orderTimeTime)/3600
   bi = list("train" = bi[which(bi$orderID <= 6053),], "class" = bi[which(bi$orderID > 6053),])
```

Add it to the clean data:
<!--- : R code (No Results in Document) -->
```{r addbatch,cache=FALSE}
   d$train = d$train %>% left_join(bi$train,by="orderID") 
   d$class = d$class %>% left_join(bi$class,by="orderID") 
```

# Creating Historical, Validation, and Training Sets
## Set 1: Random Sampling on Coupons Sets
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   sample.set = d$train[,c("orderID","couponID1","couponID2","couponID3")] %>%
      gather(couponCol,couponID,-orderID) %>%
      arrange(orderID) %>%
      select(orderID,couponID) %>%
      mutate(couponID = factor(couponID))
```

I would like to use 1/3 of my data as historical information in this case.
This means that I would like to get about 33\% of each coupons total number.

That is, for $n_i$ coupons of type $i$ we want $\frac{1}{3} n_i$ coupons of 
type $i$ in our historical pool.

<!--- cpncounts: R code (No Results in Document) -->
```{r ncounts,cache=FALSE}
   set.seed(1999)
   H1.orderIDs = d$train$orderID[sample(1:nrow(d$train))[1:round(nrow(d$train)/3)]]

   H1 = d$train[which(d$train$orderID %in% H1.orderIDs),]
   T1 = d$train[which(!(d$train$orderID %in% H1.orderIDs)),]

   set.seed(7)
   V1.orderIDs = T1$orderID[sample(1:nrow(T1))[1:round(nrow(T1)/3)]]
   V1 = T1[which(T1$orderID %in% V1.orderIDs),]
   T1 = T1[which(!(T1$orderID %in% V1.orderIDs)),]

   #feature matrix
   F1 = list("orderids" = list("h" = H1.orderIDs, "v" = V1.orderIDs), "H" = H1, "V" = V1, "T" = T1,"C" = d$class)
```

## Set 2: Random Sampling on Users
<!--- cpncounts: R code (No Results in Document) -->
```{r cpncounts,cache=FALSE}
   set.seed(1979)
   H2.userIDs = sample(unique(d$train$userID))[1:round(length(unique(d$train$userID))/3)]

   H2 = d$train[which(d$train$userID %in% H2.userIDs),]
   T2 = d$train[which(!(d$train$userID %in% H2.userIDs)),]

   set.seed(17)
   V2.userIDs = T2$userID[sample(1:nrow(T2))[1:round(nrow(T2)/3)]]
   V2 = T2[which(T2$userID %in% V2.userIDs),]
   T2 = T2[which(!(T2$userID %in% V2.userIDs)),]

   #feature matrix
   F2 = list("userids" = list("h" = H2.userIDs, "v" = V2.userIDs), "H" = H2, "V" = V2, "T" = T2, "C" = d$class)
```

## Set 3: Batch Number

<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   H3 = d$train[which(d$train$batchID %in% 1:7),]
   T3 = d$train[which(d$train$batchID == 8),]
   V3 = d$train[which(d$train$batchID == 9),]
   C3 = d$class   
   F3 = list("H" = H3, "V" = V3, "T" = T3, "C" = d$class)
```

# Write out the sets
<!--- : R code (No Results in Document) -->
```{r cache=FALSE}
   saveRDS(F1,file="../data/featureMatrix/HTVset1.rds")
   saveRDS(F2,file="../data/featureMatrix/HTVset2.rds")
   saveRDS(F3,file="../data/featureMatrix/HTVset3.rds")
```







